---
title: List of APIs
subtitle: Data
lang: en
author:
  - name: François Geerolf
    url: https://fgeerolf.com
format:
  html:
    code-fold: false
    toc: true
    theme: flatly
    embed-resources: false
editor: source
---



```{r, echo = FALSE, message = FALSE}
source(here::here("_rinit.R"))
invisible(Sys.setlocale("LC_TIME", "en_US.UTF-8"))
invisible(Sys.setenv(TZ = "America/Los_Angeles"))
api <- tribble(
  ~source, ~dataset,
  "bea",  "api",
  "bdf",  "api",
  "bis",  "api",
  "bls",  "api",
  "ecb",  "api",
  "eurostat",  "api",
  "imf", "api",
  "insee", "api",
  "oecd", "api",
  "dbnomics",  "api",
  "wdi",  "api") %>%
  arrange(source, dataset)
```

# About APIs

An Application Programming Interface (API) is an interface or communication protocol between different parts of a computer program intended to simplify the implementation and maintenance of software. Nowadays, many institutionally provided database are available through APIs.

Below, I introduce you to some of these APIs, but there are actually many more you can use.

# SDMX

## What is SDMX ?

SDMX is the Statistical Data and Metadata eXchange initiative, which is sponsored by BIS, ECB, Eurostat, IMF, OECD, UNSD and the World Bank. Data disseminated in this way is supposed to be structured in similar ways.

## SDMX in R

We shall use the ``rsdmx`` package to read in SDMX data into R statistics:

- See the `rsdmx` quickstart guide. [html](https://cran.r-project.org/web/packages/rsdmx/vignettes/quickstart.html)

## Other resources

- Eurostat explains SDMX. [html](https://ec.europa.eu/eurostat/web/sdmx-infospace/trainings-tutorials)

- The official site for the SDMX community. [html](https://sdmx.org)

- SDMX REST API: Developers' documentation. [html](https://github.com/sdmx-twg/sdmx-rest/blob/master/doc/index.md) / [Cheatsheet](https://github.com/sdmx-twg/sdmx-rest/blob/master/doc/rest_cheat_sheet.pdf?raw=true)

## List of SDMX Providers

You can easily get a list of providers through `getSDMXServiceProviders`:

```{r}
rsdmx::getSDMXServiceProviders() %>%
  as_tibble %>%
  {if (is_html_output()) datatable(., filter = 'top', rownames = F, escape = F) else .}
```

# Examples from providers

## OECD

```{r}
ig_d("oecd", "api", "IRLTLT01-FRA-JPN-DEU-GBR-GRC-USA")
```

## Eurostat

```{r}
ig_d("eurostat", "api", "example1")
```

