---
title: List of APIs
subtitle: Data
author:
  - name: François Geerolf
    url: https://fgeerolf.com
format:
  html:
    code-fold: false
    toc: true
    theme: flatly
    embed-resources: false
editor: source
---



```{r, echo = FALSE, message = FALSE}
source(here::here("_rinit.R"))
invisible(Sys.setlocale("LC_TIME", "en_US.UTF-8"))
invisible(Sys.setenv(TZ = "America/Los_Angeles"))
api <- tribble(
  ~source, ~dataset,
  "bea",  "api",
  "bdf",  "api",
  "bis",  "api",
  "bls",  "api",
  "ecb",  "api",
  "eurostat",  "api",
  "imf", "api",
  "insee", "api",
  "oecd", "api",
  "dbnomics",  "api",
  "wdi",  "api") %>%
  arrange(source, dataset)
```

# List

```{r, echo = F}
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("api.qmd")'
# cd ~/iCloud/website/data/bea; /usr/local/bin/R -e 'quarto::quarto_render("api.qmd")'
# cd ~/iCloud/website/data/bdf; /usr/local/bin/R -e 'quarto::quarto_render("api.qmd")'
# cd ~/iCloud/website/data/ecb; /usr/local/bin/R -e 'quarto::quarto_render("api.qmd")'
# cd ~/iCloud/website/data/imf; /usr/local/bin/R -e 'quarto::quarto_render("api.qmd")'
# cd ~/iCloud/website/data/insee; /usr/local/bin/R -e 'quarto::quarto_render("api.qmd")'
# cd ~/iCloud/website/data/oecd; /usr/local/bin/R -e 'quarto::quarto_render("api.qmd")'
# cd ~/iCloud/website/data/rdb; /usr/local/bin/R -e 'quarto::quarto_render("api.qmd")'
# sh ~/iCloud/website/website_short.sh
```



# `getSDMXServiceProviders`

An Application Programming Interface (API) is an interface or communication protocol between different parts of a computer program intended to simplify the implementation and maintenance of software. Nowadays, many institutionally provided database are available through APIs. Below, I introduce you to some of these APIs, but there are actually many more you can use. 

SDMX is the Statistical Data and Metadata eXchange initiative, which is sponsored by BIS, ECB, Eurostat, IMF, OECD, UNSD and the World Bank.

We will use the ``rsdmx`` package to read in SDMX data into R statistics:

- `rsdmx` quickstart guide. [html](https://cran.r-project.org/web/packages/rsdmx/vignettes/quickstart.html)

- The official site for the SDMX community. [html](https://sdmx.org)

- Eurostat explains SDMX. [html](https://ec.europa.eu/eurostat/web/sdmx-infospace/trainings-tutorials)

- SDMX REST API: Developers' documentation. [html](https://github.com/sdmx-twg/sdmx-rest/blob/master/doc/index.md) / [Cheatsheet](https://github.com/sdmx-twg/sdmx-rest/blob/master/doc/rest_cheat_sheet.pdf?raw=true)

# List of Providers

You can easily get a list of providers through `getSDMXServiceProviders`:

## Javascript

```{r}
rsdmx::getSDMXServiceProviders() %>%
  as_tibble %>%
  {if (is_html_output()) datatable(., filter = 'top', rownames = F, escape = F) else .}
```

# Examples from providers

## OECD

```{r}
ig_d("oecd", "api", "IRLTLT01-FRA-JPN-DEU-GBR-GRC-USA")
```

## Eurostat

```{r}
ig_d("eurostat", "api", "example1")
```

