---
title: Data on energy
subtitle: Data
lang: en
author:
  - name: François Geerolf
    url: https://fgeerolf.com
format:
  html:
    code-fold: false
    toc: true
    theme: flatly
    embed-resources: false
editor: source
---


```{r, echo = FALSE, message = FALSE}
source(here::here("_rinit.R"))
invisible(Sys.setlocale("LC_TIME", "en_US.UTF-8"))
invisible(Sys.setenv(TZ = "America/Los_Angeles"))
energy <- tribble(
  ~source, ~dataset,
  "ec", "WOB",
  "eurostat", "nrg_pc_202",
  "eurostat", "nrg_pc_203",
  "eurostat", "nrg_pc_203_c",
  "eurostat", "nrg_pc_203_h",
  "eurostat", "nrg_pc_203_v",
  "eurostat", "nrg_pc_204",
  "eurostat", "nrg_pc_205",
  "eurostat", "nrg_bal_c",
  "eurostat", "ei_isen_m",
  "fred",  "energy",
  "yahoo",  "energy",
  "wb", "CMO",
  "wdi", "EG.USE.PCAP.KG.OE",
  "wdi", "EG.GDP.PUSE.KO.PP.KD",
  "iea", "world_energy_balances_highlights_2022") %>%
  arrange(source, dataset)
```

# Info

```{r, echo = F}
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("energy.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("energie.qmd")'
# sh ~/iCloud/website/website_short.sh

# open https://fgeerolf.com/data/index.html
# https://fgeerolf.com/data/energy.html
# open https://fgeerolf.com/data/energy.html
# open https://fgeerolf.com/data/energie.html
```


## Bibliography

- Geerolf, François. « The “Baqaee-Farhi approach” and a russian gas embargo », Revue de l'OFCE, vol. 179, no. 4, 2022, pp. 143-165. [[pdf](https://www.ofce.sciences-po.fr/pdf/revue/4-179OFCE.pdf)] [[slides](https://fgeerolf.com/russiangas-slides.pdf)] [[html](https://www.cairn.info/revue-de-l-ofce-2022-4-page-143.htm?contenu=article)]

# Weekly gas prices

```{r, echo = F}
# cd ~/iCloud/website/data/ec; /usr/local/bin/R -f WOB.R; /usr/local/bin/R -e 'quarto::quarto_render("WOB.qmd")'
# cd ~/iCloud/website/data/ec
# sh ~/iCloud/website/website_short.sh
```

## Automotive gas oil

### All

```{r}
ig_d("ec", "WOB", "automotive-gas-oil-FR-DE-ES")
```

### 3 months

```{r}
ig_d("ec", "WOB", "automotive-gas-oil-FR-DE-ES-IT-3-months")
```



## Heating gas oil

```{r}
ig_d("ec", "WOB", "heating-gas-oil-FR-DE-ES")
```


## Euro super

```{r}
ig_d("ec", "WOB", "euro-super-95-FR-DE-ES")
```

# TTF

```{r, echo = F}
# cd ~/iCloud/website/data/yahoo; /usr/local/bin/R -f "energy.R"; /usr/local/bin/R -e 'quarto::quarto_render("energy.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## All

```{r}
ig_d("yahoo", "energy", "TTF")
```

## 2021-

```{r}
ig_d("yahoo", "energy", "TTF-2021")
```



## Log

```{r}
ig_d("yahoo", "energy", "TTF-log")
```

## Log, 2021-

```{r}
ig_d("yahoo", "energy", "TTF-log-2021")
```

# Weekly Oil prices, Europe

```{r, echo = F}
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -f "energy.R"; /usr/local/bin/R -e 'quarto::quarto_render("energy.qmd")'
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
```

## All

```{r}
ig_d("fred", "energy", "MHHNGSP-PNGASEUUSDM-1990")
```


## 2017-


# Natural Gas

## Fred

```{r, echo = F}
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -f "energy.R"; /usr/local/bin/R -e 'quarto::quarto_render("energy.qmd")'
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
# sh ~/iCloud/website/website_short.sh
```

### 1990-

```{r}
ig_d("fred", "energy", "MHHNGSP-PNGASEUUSDM-1990")
```

### Last 10 years

```{r}
ig_d("fred", "energy", "MHHNGSP-PNGASEUUSDM-last-10-years")
```



## World Bank

```{r, echo = F}
# cd ~/iCloud/website/data/wb; /usr/local/bin/R -f "CMO.R"; /usr/local/bin/R -e 'quarto::quarto_render("CMO.qmd")'
# sh ~/iCloud/website/website_short.sh
```

### 2000-

```{r}
ig_d("wb", "CMO", "natural-gas-nominal-log-2000")
```



# Inflation Expectations and Gas Prices

```{r, echo = F}
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -f "energy.R"; /usr/local/bin/R -e 'quarto::quarto_render("energy.qmd")'
# cd ~/iCloud/website/data/fred
# sh ~/iCloud/website/website_short.sh
```

## 1990-

```{r}
ig_d("fred", "energy", "GASREGW-MICH-1990")
```

# Gas prices for households consumers

```{r, echo = F}
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R nrg_pc_202; /usr/local/bin/R -e 'quarto::quarto_render("nrg_pc_202.qmd")'
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
# cd ~/iCloud/website/data/eurostat
# sh ~/iCloud/website/website_short.sh
```

## All

```{r}
ig_d("eurostat", "nrg_pc_202", "4141901-ITAX-XTAX-FR-DE-IR-ES")
```



## 2016-

```{r}
ig_d("eurostat", "nrg_pc_202", "4141901-ITAX-XTAX-FR-DE-IR-ES-2016")
```



# Electricity prices for households consumers

```{r, echo = F}
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R nrg_pc_204; /usr/local/bin/R -e 'quarto::quarto_render("nrg_pc_204.qmd")'
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _metadata_one.R consom
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/R -e 'quarto::quarto_render("nrg_pc_202.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## All

```{r}
ig_d("eurostat", "nrg_pc_204", "4161902-ITAX-XTAX-FR-DE-IR-ES")
```

## 2021-

```{r}
ig_d("eurostat", "nrg_pc_204", "4161901-ITAX-XTAX-FR-DE-EA-ES-2020")
```


## Low Consumption

```{r}
ig_d("eurostat", "nrg_pc_204", "4161901-3-bars-FR-DE-EA-ES")
```


## High Consumption

```{r}
ig_d("eurostat", "nrg_pc_204", "4161905-3-bars-FR-DE-EA-ES")
```



## Germany

```{r}
ig_d("eurostat", "nrg_pc_204", "DE-KWH-EUR")
```



## France

```{r}
ig_d("eurostat", "nrg_pc_204", "FR-KWH-EUR")
```
