---
title: Is there slack in the Euro area?
metadata-files:
  - _common.yml
---

```{r, echo = FALSE, message = FALSE}
source(here::here("_rinit.R"))
invisible(Sys.setlocale("LC_TIME", "en_US.UTF-8"))
invisible(Sys.setenv(TZ = "America/Los_Angeles"))
knitr::opts_chunk$set(echo = T)
`europe-slack` <- tribble(
  ~source, ~dataset,
  "ameco", "AVGDGP",
  "ameco", "ZNAWRU",
  "oecd", "EO_GAP",
  "oecd", "INVPT_I",
  "eurostat", "lfsi_sla_q",
  "eurostat", "une_rt_m",
  "eurostat", "namq_10_lp_ulc",
  "eurostat", "tipslm80",
  "eurostat", "edat_lfse_18",
  "eurostat", "lfsa_urgaed",
  "eurostat", "migr_emi2",
  "eurostat", "ei_bsin_m_r2",
  "ecb", "INW",
  "ecb", "EWT",
  "ecb", "ICP") %>%
  arrange(source, dataset)
```

# Info

```{r, echo = F}
# Rebuild the individual dataset pages (each holds the labelled chunk that
# ig_d() below embeds), then this page:
# cd ~/iCloud/website/data; Rscript --vanilla _update_qmd_folder.R ameco    only=AVGDGP.qmd
# cd ~/iCloud/website/data; Rscript --vanilla _update_qmd_folder.R ameco    only=ZNAWRU.qmd
# cd ~/iCloud/website/data; Rscript --vanilla _update_qmd_folder.R oecd     only=EO_GAP.qmd
# cd ~/iCloud/website/data; Rscript --vanilla _update_qmd_folder.R oecd     only=INVPT_I.qmd
# cd ~/iCloud/website/data; Rscript --vanilla _update_qmd_folder.R eurostat only=lfsi_sla_q.qmd
# cd ~/iCloud/website/data; Rscript --vanilla _update_qmd_folder.R eurostat only=une_rt_m.qmd
# cd ~/iCloud/website/data; Rscript --vanilla _update_qmd_folder.R eurostat only=namq_10_lp_ulc.qmd
# cd ~/iCloud/website/data; Rscript --vanilla _update_qmd_folder.R eurostat only=tipslm80.qmd
# cd ~/iCloud/website/data; Rscript --vanilla _update_qmd_folder.R eurostat only=edat_lfse_18.qmd
# cd ~/iCloud/website/data; Rscript --vanilla _update_qmd_folder.R eurostat only=lfsa_urgaed.qmd
# cd ~/iCloud/website/data; Rscript --vanilla _update_qmd_folder.R eurostat only=migr_emi2.qmd
# cd ~/iCloud/website/data; Rscript --vanilla _update_qmd_folder.R eurostat only=ei_bsin_m_r2.qmd
# cd ~/iCloud/website/data; Rscript --vanilla _update_qmd_folder.R ecb      only=INW.qmd
# cd ~/iCloud/website/data; Rscript --vanilla _update_qmd_folder.R ecb      only=EWT.qmd
# cd ~/iCloud/website/data; Rscript --vanilla _update_qmd_folder.R ecb      only=ICP.qmd
# sh ~/iCloud/website/website_short.sh; open https://fgeerolf.com/data/europe-slack.html
```

**Slack** — the gap between what the economy *does* produce and what it *could*
produce without pushing up inflation — is not observed directly. This page
gathers the pieces of evidence that, taken together, suggest the euro area
operated with substantial and persistent slack for most of the decade that
followed the 2008 crisis, and that pockets of it are still visible.

The individual charts live on their own dataset pages; here they are lined up
by theme.

# Output gap and potential output

## AMECO: output gap, euro area and the big four

The European Commission's own accounts put the euro area below potential from
2009 to 2019, with double-digit gaps in Spain and Italy at the trough.

```{r}
ig_d("ameco", "AVGDGP", "EA19-DEU-FRA-ITA-ESP")
```

## OECD: euro area vs the United States

The euro area suffered a *double dip* (2011-2013) that the United States did
not: activity fell back below potential a second time as fiscal policy
tightened and the sovereign-debt crisis spread.

```{r}
ig_d("oecd", "EO_GAP", "EA17-USA")
```

# Unemployment and the unemployment gap

## Euro area unemployment since 1998

```{r}
ig_d("eurostat", "une_rt_m", "EA21-since-1998")
```

## Euro area and the big four

The aggregate hides a wide and long-lasting dispersion: Spanish and Italian
unemployment stayed in double digits for most of the 2010s.

```{r}
ig_d("eurostat", "une_rt_m", "EA21-FR-DE-IT-ES-2002")
```

## Actual unemployment vs the NAWRU

AMECO's estimate of *structural* unemployment (the NAWRU) drifts up whenever
actual unemployment rises, mechanically re-labelling cyclical joblessness as
structural and shrinking the measured amount of slack. Even so, actual
unemployment stayed above the NAWRU from 2009 to 2018.

```{r}
ig_d("ameco", "ZNAWRU", "EA19-unemp-vs-nawru")
```

# Broad labour-market slack

## Eurostat labour-market slack: euro area and the big four

The unemployment rate understates slack. Eurostat's broad measure adds
involuntary part-timers, people available to work but not searching, and
people searching but not immediately available. On that gauge roughly one in
seven members of the extended euro-area labour force was under-used even in
2018-2019.

```{r}
ig_d("eurostat", "lfsi_sla_q", "SLACK-EA20-FR-DE-ES-IT")
```

## Slack the unemployment rate misses

On top of the unemployed, three groups make up broad slack: people working
part-time who want more hours, people available to work but not currently
searching, and people searching but not immediately available. Together they
add several percentage points of the extended labour force.

```{r}
ig_d("eurostat", "lfsi_sla_q", "EA20-slack-components")
```

## Involuntary part-time work

Involuntary part-time employment — people working short hours because they
cannot find full-time work — roughly doubled in France, Italy, Spain and
Greece after 2008 while it *fell* in Germany.

```{r}
ig_d("oecd", "INVPT_I", "SHINV-EMP-FRA-DEU-ITA-ESP-GRC")
```



# Demand adressed to firms

## Assessment of order-book levels, euro-area industry

In the European Commission's industry survey, the balance of firms judging
their order books "above" vs "below" normal stayed deeply negative from 2008
through 2013, briefly recovered around 2017-2018, and has turned negative
again since 2023: for long stretches the binding constraint has been
customers, not capacity.

```{r}
ig_d("eurostat", "ei_bsin_m_r2", "BS-IOB-EA20-2000")
```

# Skills under-used

## Euro area unemployment by education level

Slack reached the highly educated too: the unemployment rate of the
tertiary-educated in the euro area rose after 2008 and stayed elevated,
a sign that the shortfall in jobs was economy-wide rather than a
qualifications problem.

```{r}
ig_d("eurostat", "lfsa_urgaed", "EA-unemployment-by-education")
```

# Young people: unemployment, inactivity, emigration

## Youth unemployment

```{r}
ig_d("eurostat", "tipslm80", "EA20-EL-ES-IT-DE")
```

## NEET rate (15-29): not in employment, education or training

```{r}
ig_d("eurostat", "edat_lfse_18", "NEET-EA21-IT-ES-EL-DE")
```

## Emigration of young adults from southern Europe

When domestic labour markets stay slack, workers leave. Emigration of
20-34 year-olds from Italy rose through the 2010s and is still climbing;
Spain and Greece spiked during the crisis years. (Spain's series also
reflects large numbers of foreign nationals leaving again, so read the
level with care — the direction is the point.)

```{r}
ig_d("eurostat", "migr_emi2", "emigration-young-south")
```

# Slack through tight credit

## Bank Lending Survey

```{r}
ig_d("ecb", "BLS", "BLS.Q.U2.ALL.Z.H.H-C.B3.ZZ.D.WFNET")
```

# Datasets

```{r, echo = F}
`europe-slack` |>
  source_dataset_file_updates()
```
