---
title: Europe in Numbers
metadata-files: 
  - _common.yml
---


```{r, echo = FALSE, message = FALSE}
source(here::here("_rinit.R"))
invisible(Sys.setlocale("LC_TIME", "en_US.UTF-8"))
invisible(Sys.setenv(TZ = "America/Los_Angeles"))
`europe` <-tribble(
  ~source, ~dataset,
  "eurostat", "bop_gdp6_q",
  "eurostat",  "nama_10_a10_e",
  "eurostat",  "namq_10_a10_e",
  "eurostat",  "nama_10_a10",
  "eurostat",  "namq_10_a10",
  "eurostat",  "nama_10_gdp",
  "eurostat",  "namq_10_gdp",
  "eurostat",  "nama_10_lp_ulc",
  "eurostat",  "namq_10_lp_ulc",
  "eurostat",  "namq_10_pc",
  "eurostat", "nasa_10_nf_tr",
  "eurostat", "nasq_10_nf_tr",
  "eurostat", "tipsii40") %>%
  arrange(source, dataset)
```


# Related themes

```{r, echo = F}
tribble(~ theme,
        "monetary-policy", 
        "inflation-europe",
        "euro",
        "germany",
        "poland",
        "greece",
        "italy",
        "france") |>
  theme_file_updates()
```

# Related papers

```{r, echo = F}
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("europe.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("macro-france.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("macro.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("interest-rates.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("monetary-policy.qmd")'
# sh ~/iCloud/website/website_short.sh; open https://fgeerolf.com/data/macro-france.html
# sh ~/iCloud/website/website_short.sh; open https://fgeerolf.com/data/europe.html
# sh ~/iCloud/website/website_short.sh; open https://fgeerolf.com/data/inflation-france.html
# sh ~/iCloud/website/website_short.sh
```


## English

{{< include ../publications/en/Blot2025.qmd >}}

{{< include ../publications/en/Blot2023d.qmd >}}

{{< include ../publications/en/Geerolf2023b.qmd >}}

{{< include ../publications/en/Blot2023c.qmd >}}

{{< include ../publications/en/Blot2023b.qmd >}}

{{< include ../publications/en/Blot2023a.qmd >}}

{{< include ../publications/en/Blot2022.qmd >}}


## French

{{< include ../publications/fr/Geerolf2025a.qmd >}}

{{< include ../publications/fr/Blot2025.qmd >}}

{{< include ../publications/fr/Geerolf2024d.qmd >}}

{{< include ../public-debate/fr/Geerolf2024b.qmd >}}

{{< include ../publications/fr/Geerolf2023b.qmd >}}

{{< include ../publications/fr/Geerolf2023a.qmd >}}

{{< include ../publications/fr/Allegre2022.qmd >}}

{{< include ../publications/fr/Creel2022.qmd >}}

# Relative importance

## PIB relatif

```{r}
ig_d("wdi", "NY.GDP.MKTP.CD", "US-CN-EU")
```

## GDP per capita

```{r}
ig_d("eurostat", "nama_10_pc", "FR-EU-PL-HU-PL-EL-IT")
```

## Compare

```{r}
ig_d("eurostat", "nama_10_pc", "FR-EU-PL-HU-PL-EL-IT-using-groups-linear")
```




# GDP Horse races

```{r, echo = F}
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R namq_10_gdp; /usr/local/bin/R -e 'quarto::quarto_render("namq_10_gdp.qmd")'
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R namq_10_a10_e; /usr/local/bin/R -e 'quarto::quarto_render("namq_10_a10_e.qmd")'
# cd ~/iCloud/website/data/wdi; /usr/local/bin/Rscript --vanilla _dl_one_value.R NY.GDP.PCAP.PP.CD; /usr/local/bin/R -e 'quarto::quarto_render("NY.GDP.PCAP.PP.CD.qmd")'
# cd ~/iCloud/website/data/wdi; /usr/local/bin/Rscript --vanilla _dl_one_value.R NY.GDP.PCAP.CD; /usr/local/bin/R -e 'quarto::quarto_render("NY.GDP.PCAP.CD.qmd")'
# cd ~/iCloud/website/data/oecd; /usr/local/bin/R -f QNA_9.R; /usr/local/bin/R -e 'quarto::quarto_render("QNA_live.qmd")'; /usr/local/bin/R -e 'quarto::quarto_render("QNA_live.qmd")'
# cd ~/iCloud/website/data/oecd; /usr/local/bin/R -e 'quarto::quarto_render("QNA_live.qmd")'
# sh ~/iCloud/website/website_short.sh
```


## Europe, U.S., OCDE



## Europe, U.S.

### OECD

#### GDP


```{r}
ig_d("oecd", "QNA_EXPENDITURE_CAPITA", "USA-EA20-2000-new-english")
```

### WDI (2008-)

#### PIB

##### Current Dollar

```{r}
ig_d("wdi", "NY.GDP.MKTP.CD", "XC-US-PIB-dollars")
```



##### 2015 Dollars

```{r}
ig_d("wdi", "NY.GDP.MKTP.KD", "XC-US-PIB-dollars")
```

##### Current PPP Dollars

```{r}
ig_d("wdi", "NY.GDP.MKTP.PP.CD", "XC-US-PIB-dollars")
```


##### 2015 PPP Dollars

```{r}
ig_d("wdi", "NY.GDP.MKTP.PP.KD", "XC-US-PIB-dollars")
```



#### PIB/habitant

##### Current Dollar

```{r}
ig_d("wdi", "NY.GDP.PCAP.CD", "XC-US-PIB-dollars")
```



##### 2015 Dollars

```{r}
ig_d("wdi", "NY.GDP.PCAP.KD", "XC-US-PIB-dollars")
```

##### Current PPP Dollars

```{r}
ig_d("wdi", "NY.GDP.PCAP.PP.CD", "XC-US-PIB-dollars")
```


##### 2015 PPP Dollars

```{r}
ig_d("wdi", "NY.GDP.PCAP.PP.KD", "XC-US-PIB-dollars")
```



## Germany, France, Italy, Spain

### Since Covid-19

```{r}
ig_d("eurostat", "namq_10_gdp", "DE-IT-ES-FR-2019")
```



### 1996-

```{r}
ig_d("eurostat", "namq_10_gdp", "B1GQ-SCA-CLV10MEUR-DE-EA19-FR-IT-1996")
```


## Germany, France, Italy, Spain

```{r}
ig_d("eurostat", "namq_10_gdp", "DE-IT-ES-FR-2019")
```

# Unemployment

```{r, echo = F}
# cd ~/iCloud/website/data/oecd; /usr/local/bin/R -f STLABOUR_7.R; /usr/local/bin/R -e 'quarto::quarto_render("STLABOUR.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## Europe, France, United States

### 1990-

```{r}
ig_d("oecd", "STLABOUR", "LRHUTTTT-M-USA-EA20-FRA-1990")
```

### 2005-

```{r}
ig_d("oecd", "STLABOUR", "LRHUTTTT-M-USA-EA19-FRA-2005")
```

## Germany, France, Italy

### All

```{r}
ig_d("oecd", "STLABOUR", "LRHUTTTT-Q-DEU-FRA-ITA")
```


# Employment in Manufacturing

```{r, echo = F}
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R namq_10_a10_e; /usr/local/bin/R -e 'quarto::quarto_render("namq_10_a10_e.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## France, Italy, Germany

```{r}
ig_d("eurostat", "namq_10_a10_e", "C-TOTAL-FR-DE-IT-1995-flags")
```

## France, Italy, Germany, Spain, Europe

```{r}
ig_d("eurostat", "namq_10_a10_e", "C-TOTAL-FR-DE-IT-ES-EA-1995-flags")
```

## Spain, Netherlands, Portugal

```{r}
ig_d("eurostat", "namq_10_a10_e", "C-TOTAL-ES-NL-PT-1995-flags")
```

# Current account balance

```{r, echo = F}
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R bop_gdp6_q; /usr/local/bin/R -e 'quarto::quarto_render("bop_gdp6_q.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## All

```{r}
ig_d("eurostat", "bop_gdp6_q", "DE-ES-FR-IT-NL-EA20")
```

## 2012

```{r}
ig_d("eurostat", "bop_gdp6_q", "DE-ES-FR-IT-NL-EA20-2012")
```




# Net international investment position

```{r, echo = F}
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R tipsii40; /usr/local/bin/R -e 'quarto::quarto_render("tipsii40.qmd")'
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R bop_iip6_q; /usr/local/bin/R -e 'quarto::quarto_render("bop_iip6_q.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## Bn€

### Main Europe


```{r}
ig_d("eurostat", "bop_iip6_q", "FANENDI-FR-DE-EA20-ES-NL-IT")
```

### France, Germany, Europe

```{r}
ig_d("eurostat", "bop_iip6_q", "FANENDI-FR-DE-EA20")
```

## % of GDP

### Germany, Spain, France, Italy, Netherlands

```{r}
ig_d("eurostat", "tipsii40", "DE-ES-FR-IT-NL-2000")
```

### With Greece

```{r}
ig_d("eurostat", "tipsii40", "DE-BE-FR-IT-NL-ES-EL")
```




# Commerce extérieur

```{r, echo = F}
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R tipsbp20; /usr/local/bin/R -e 'quarto::quarto_render("tipsbp20.qmd")'
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R namq_10_gdp; /usr/local/bin/R -e 'quarto::quarto_render("namq_10_gdp.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## Trimestriel

```{r}
ig_d("eurostat", "namq_10_gdp", "P6-P7-SCA-FR-DE-IT-EA-ES-1998")
```



## Moyenne 3 ans

```{r}
ig_d("eurostat", "tipsbp20", "mean-sd-EU27-FR-DE")
```




# Datasets

```{r, echo = F}
`europe` |>
  source_dataset_file_updates()
```

# Related themes



```{r, echo = F}
tribble(~ theme,
        "greece",
        "poland") |>
  theme_file_updates()
```