---
title: Germany by the Numbers
metadata-files: 
  - _common.yml
---


```{r, echo = FALSE, message = FALSE}
source(here::here("_rinit.R"))
invisible(Sys.setlocale("LC_TIME", "en_US.UTF-8"))
invisible(Sys.setenv(TZ = "America/Los_Angeles"))
`germany` <-tribble(
  ~source, ~dataset,
  "oecd", "QNA",
  "wdi", "NY.GDP.PCAP.PP.CD") %>%
  arrange(source, dataset)
```

# Related themes

```{r, echo = F}
tribble(~ theme,
        "monetary-policy", 
        "europe",
        "inflation-europe",
        "poland",
        "greece",
        "italy",
        "france") |>
  theme_file_updates()
```

```{r, echo = F}
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("germany.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("greece.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("macro-us.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("macro-france.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("macro.qmd")'
# sh ~/iCloud/website/website_short.sh; open https://fgeerolf.com/data/macro-france.html
# sh ~/iCloud/website/website_short.sh; open https://fgeerolf.com/data/inflation-france.html
# sh ~/iCloud/website/website_short.sh
```

# Investment

```{r, echo = F}
# cd ~/iCloud/website/data/wdi; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
# cd ~/iCloud/website/data/oecd; /usr/local/bin/R -f QNA_9.R
# cd ~/iCloud/website/data/oecd; /usr/local/bin/R -e 'quarto::quarto_render("QNA_live.qmd")'
# cd ~/iCloud/website/data/oecd; /usr/local/bin/R -e 'quarto::quarto_render("QNA.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## Investment and Saving

```{r}
ig_d("oecd", "QNA", "DEU-S-I-french")
```


## Total Economy

```{r}
ig_d("oecd", "SNA_TABLE14A", "NFP5P-DEU")
```

## Government

```{r}
ig_d("oecd", "SNA_TABLE14A", "NFK1R-NFP5P-S13-FRA-USA-DEU")
```

```{r}
ig_d("oecd", "SNA_TABLE8A", "DEU")
```


# Current Accounts

## CA, Goods, Goods and services

```{r}
ig_d("eurostat", "bop_c6_q", "DE-CA-GS-G")
```


## Net Exports

```{r}
ig_d("oecd", "QNA_EXPENDITURE_NATIO_CURR", "P6-P7-B1GQ-DEU")
```




# Employment

```{r, echo = F}
# cd ~/iCloud/website/data/wdi; /usr/local/bin/Rscript --vanilla _dl_one_value.R NY.GDP.PCAP.PP.CD
# cd ~/iCloud/website/data/wdi; /usr/local/bin/Rscript --vanilla _dl_one_value.R NY.GDP.PCAP.CD
# cd ~/iCloud/website/data/wdi; /usr/local/bin/R -e 'quarto::quarto_render("NY.GDP.PCAP.PP.CD.qmd")'
# cd ~/iCloud/website/data/wdi; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
# cd ~/iCloud/website/data/oecd; /usr/local/bin/R -f QNA_9.R
# cd ~/iCloud/website/data/oecd; /usr/local/bin/R -e 'quarto::quarto_render("QNA_live.qmd")'
# cd ~/iCloud/website/data/oecd; /usr/local/bin/R -e 'quarto::quarto_render("QNA.qmd")'
# cd ~/iCloud/website/data/oecd; /usr/local/bin/R -f QNA_9.R
# cd ~/iCloud/website/data/oecd; /usr/local/bin/R -e 'quarto::quarto_render("QNA_live.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## France, Germany

```{r}
ig_d("oecd", "DP_LIVE", "PARTEMP-DEU-FRA-french")
```

# GDP

```{r, echo = F}
# cd ~/iCloud/website/data/wdi; /usr/local/bin/Rscript --vanilla _dl_one_value.R NY.GDP.PCAP.PP.KD
# cd ~/iCloud/website/data/wdi; /usr/local/bin/R -e 'quarto::quarto_render("NY.GDP.PCAP.PP.KD.qmd")'
# cd ~/iCloud/website/data/wdi; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## France VS Germany

```{r}
ig_d("wdi", "NY.GDP.PCAP.PP.KD", "FR-DE-index")
```





# Manufacturing

```{r, echo = F}
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R sts_intvnd_m
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/R -e 'quarto::quarto_render("sts_intvnd_m.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## Manufacturing

```{r}
ig_d("eurostat", "sts_intvnd_m", "C-DE-1995")
```

# Average Hours Worked Annually by Worker

```{r ANHRS-TE}
ig_d("oecd", "ANHRS", "TE-DEU-FRA-ITA")
```

# Competitiveness: General Indicators

## CPIDR - Indicator of competitiveness based on relative consumer prices

```{r CPIDR}
ig_d("oecd", "EO", "CPIDR-FRA-DEU")
```



## ULCDR - Indicator of competitiveness based on relative unit labour costs in total economy

```{r ULCDR}
ig_d("oecd", "EO", "ULCDR-FRA-DEU")
```

# Competitiveness: Unit Labor cost

## Total Economy

```{r ULC-ANN-ULABUL99-01}
ig_d("oecd", "ULC_ANN", "ULABUL99-01-FRA-DEU")
```


## Manufacturing

```{r ULC-ANN-ULABUL99-02}
ig_d("oecd", "ULC_ANN", "ULABUL99-02-FRA-DEU")
```


## Industry

```{r ULC-ANN-ULABUL99-03}
ig_d("oecd", "ULC_ANN", "ULABUL99-03-FRA-DEU")
```


## Construction

```{r ULC-ANN-ULABUL99-04}
ig_d("oecd", "ULC_ANN", "ULABUL99-04-FRA-DEU")
```


## Trade, transport and communication (G_I)

```{r ULC-ANN-ULABUL99-05}
ig_d("oecd", "ULC_ANN", "ULABUL99-05-FRA-DEU")
```



## Financial and business services

```{r ULC-ANN-ULABUL99-06}
ig_d("oecd", "ULC_ANN", "ULABUL99-06-FRA-DEU")
```


## Market services

```{r ULC-ANN-ULABUL99-07}
ig_d("oecd", "ULC_ANN", "ULABUL99-07-FRA-DEU")
```


## Business sector excl. Agriculture

```{r ULC-ANN-ULABUL99-08}
ig_d("oecd", "ULC_ANN", "ULABUL99-08-FRA-DEU")
```


# Competitiveness: Exchange Rate Adjusted ULC

## Total Economy

```{r ULC-ANN-ULAIEU99-01}
ig_d("oecd", "ULC_ANN", "ULAIEU99-01-FRA-DEU")
```


## Manufacturing

```{r ULC-ANN-ULAIEU99-02}
ig_d("oecd", "ULC_ANN", "ULAIEU99-02-FRA-DEU")
```


## Industry

```{r ULC-ANN-ULAIEU99-03}
ig_d("oecd", "ULC_ANN", "ULAIEU99-03-FRA-DEU")
```





## Construction

```{r ULC-ANN-ULAIEU99-04}
ig_d("oecd", "ULC_ANN", "ULAIEU99-04-FRA-DEU")
```


## Trade, transport and communication (G_I)

```{r ULC-ANN-ULAIEU99-05}
ig_d("oecd", "ULC_ANN", "ULAIEU99-05-FRA-DEU")
```



## Financial and business services

```{r ULC-ANN-ULAIEU99-06}
ig_d("oecd", "ULC_ANN", "ULAIEU99-06-FRA-DEU")
```


## Market services

```{r ULC-ANN-ULAIEU99-07}
ig_d("oecd", "ULC_ANN", "ULAIEU99-07-FRA-DEU")
```


## Business sector excl. Agriculture

```{r ULC-ANN-ULAIEU99-08}
ig_d("oecd", "ULC_ANN", "ULAIEU99-08-FRA-DEU")
```





# Competitiveness: Labour Income Share (Real ULC)

## Total Economy

```{r ULC-ANN-ULAIRU99-01}
ig_d("oecd", "ULC_ANN", "ULAIRU99-01-FRA-DEU")
```


## Manufacturing

```{r ULC-ANN-ULAIRU99-02}
ig_d("oecd", "ULC_ANN", "ULAIRU99-02-FRA-DEU")
```


## Industry

```{r ULC-ANN-ULAIRU99-03}
ig_d("oecd", "ULC_ANN", "ULAIRU99-03-FRA-DEU")
```





## Construction

```{r ULC-ANN-ULAIRU99-04}
ig_d("oecd", "ULC_ANN", "ULAIRU99-04-FRA-DEU")
```


## Trade, transport and communication (G_I)

```{r ULC-ANN-ULAIRU99-05}
ig_d("oecd", "ULC_ANN", "ULAIRU99-05-FRA-DEU")
```



## Financial and business services

```{r ULC-ANN-ULAIRU99-06}
ig_d("oecd", "ULC_ANN", "ULAIRU99-06-FRA-DEU")
```


## Market services

```{r ULC-ANN-ULAIRU99-07}
ig_d("oecd", "ULC_ANN", "ULAIRU99-07-FRA-DEU")
```


## Business sector excl. Agriculture

```{r ULC-ANN-ULAIRU99-08}
ig_d("oecd", "ULC_ANN", "ULAIRU99-08-FRA-DEU")
```



# Average Annual Wages

## Current prices in NCU

```{r AV-AN-WAGE-CPNCU}
ig_d("oecd", "AV_AN_WAGE", "CPNCU-FRA-DEU")

```


## 2017 constant prices and NCU

```{r AV-AN-WAGE-CNPNCU}
ig_d("oecd", "AV_AN_WAGE", "CNPNCU-FRA-DEU")
```

# Current Account

(ref:B6BLTT02) <span style="font-variant:small-caps;">Net Lending / Net Borrowing - Total Economy</span>

```{r B6BLTT02, fig.cap="(ref:B6BLTT02)"}
ig_d("oecd", "MEI_BOP6", "B6BLTT02-FRA-DEU")
```



# Saving

## Net Saving - Total

(ref:B8NS) <span style="font-variant:small-caps;">Net saving , TOTAL (% of GDP)</span>

```{r B8NS, fig.cap="(ref:B8NS)"}
ig_d("oecd", "NAAG", "B8NS-FRA-DEU")
```


## Net Saving of General Government

(ref:B8NS13S) <span style="font-variant:small-caps;">Net saving of General Government (% of GDP)</span>

```{r B8NS13S, fig.cap="(ref:B8NS13S)"}
ig_d("oecd", "NAAG", "B8NS13S-FRA-DEU")
```

## Corporate Saving


(ref:B9S14-S15S) <span style="font-variant:small-caps;">Corporate Saving</span>

```{r B9S14-S15S, fig.cap="(ref:B9S14-S15S)"}
ig_d("oecd", "NAAG", "B9S14-S15S-FRA-DEU")
```



## Net Lending / Net Borrowing - Total Economy

(ref:B9S1S) <span style="font-variant:small-caps;">Net lending/net borrowing, Total economy</span>

```{r B9S1S, fig.cap="(ref:B9S1S)"}
ig_d("oecd", "NAAG", "B9S1S-FRA-DEU")
```



## Net lending/net borrowing, Corporations

(ref:B9S11-S12S) <span style="font-variant:small-caps;">Net lending/net borrowing, Corporations</span>

```{r B9S11-S12S, fig.cap="(ref:B9S11-S12S)"}
ig_d("oecd", "NAAG", "B9S11-S12S-FRA-DEU")
```



# Slack in the Labor Market

## Part Time Work

```{r EMP5-AGE}
ig_d("oecd", "GENDER_EMP", "EMP5-DEU-AGE")
```



## Involuntary Part Time Work

```{r EMP6-AGE}
ig_d("oecd", "GENDER_EMP", "EMP6-DEU-AGE")
```


## Involuntary Part Time Employment - WOMEN

```{r EMP6-AGE-WOMEN}
ig_d("oecd", "GENDER_EMP", "EMP6-DEU-AGE-WOMEN")
```


## Involuntary Part Time Employment - MEN

```{r EMP6-AGE-MEN}
ig_d("oecd", "GENDER_EMP", "EMP6-DEU-AGE-MEN")
```

## Labor Force Participation Rate

```{r LFPR-2554}
ig_d("oecd", "LFS_SEXAGE_I_R", "LFPR-2554")
```



```{r LFPR-1564}
ig_d("oecd", "LFS_SEXAGE_I_R", "LFPR-1564")
```

## Labor Force Participation Rate - 65+

```{r LFPR-6599}
ig_d("oecd", "LFS_SEXAGE_I_R", "LFPR-6599")
```


```{r LFPR-6569}
ig_d("oecd", "LFS_SEXAGE_I_R", "LFPR-6569")
```



```{r EPR-6569}
ig_d("oecd", "LFS_SEXAGE_I_R", "EPR-6569")
```

## Employment / Population Ratio

```{r EPR-2554}
ig_d("oecd", "LFS_SEXAGE_I_R", "EPR-2554")
```

```{r EPR-2554-DEU}
ig_d("oecd", "LFS_SEXAGE_I_R", "EPR-2554-DEU")
```


## Labor Force Participation - Women

```{r LFPR-2554-WOMEN}
ig_d("oecd", "LFS_SEXAGE_I_R", "LFPR-2554-WOMEN")
```




## Part Time Employment Rate - DP_LIVE

```{r DP-LIVE-PARTEMP}
ig_d("oecd", "DP_LIVE", "PARTEMP-DEU-JPN-NLD")
```

# Unemployment: Net Replacement Rates

```{r NRR-unemployment}
ig_d("oecd", "NRR", "DEU-AW-SINGLE-1")
```

# Pension Plans

## Pension Funds


```{r QASA-TABLE720R-RS129-LBF90NC}
ig_d("oecd", "QASA_TABLE720R", "RS1-CAR-DEU")
```

## Pension plans managed by autonomous pension funds

```{r}
ig_d("oecd", "7HA_A_Q", "AF612-DEU")
```


## Gross Pension Replacement Rates - MEN

```{r GPENSION-MEN}
ig_d("oecd", "DP_LIVE", "GPENSION-MEN")
```


## Gross Pension Replacement Rates - WOMEN

```{r GPENSION-WOMEN}
ig_d("oecd", "DP_LIVE", "GPENSION-WOMEN")
```




# Eurostat - D10 / D1

```{r ILC-DI01}
ig_d("eurostat", "ilc_di01", "ILC-DI01")
```




```{r ILC-eurostat-D9D1}
ig_d("eurostat", "ilc_di01", "ILC-eurostat-D9D1")
```


# Eurostat - poverty

```{r LI-R-M60}
ig_d("eurostat", "ilc_li02", "LI-R-M60")
```

```{r LI-R-M40}
ig_d("eurostat", "ilc_li02", "LI-R-M40")
```


# Poverty

## PVT5A

```{r PVT5A}
ig_d("oecd", "IDD", "PVT5A-DEU-FRA")
```



## PVT5B


```{r PVT5B}
ig_d("oecd", "IDD", "PVT5B-DEU-FRA")
``` 




## PALMA


```{r PALMA}
ig_d("oecd", "IDD", "PALMA-DEU-FRA")
```



## PVTAATOTAL

```{r PVTAATOTAL}
ig_d("oecd", "IDD", "PVTAATOTAL-DEU-FRA")
```

## GINIB

```{r GINIB}
ig_d("oecd", "IDD", "GINIB-DEU-FRA")
```

# Tax Rates

## Corporate Income- Germany

```{r statutory-corporate}
ig_d("oecd", "CTS_CIT", "DEU")
```



## Effective Tax Rates on Increasing Labor Hours

```{r effective-tax-rate-increase-labor}
ig_d("oecd", "METR", "SINGLE-AW-0-DEU")
```


## Effective Tax Rates on Increasing Labor Hours (No Housing)

```{r effective-tax-rate-increase-labor-no-housing}
ig_d("oecd", "METR", "SINGLE-AW-1-DEU")
```

## Personal Income Tax Rates

```{r}
ig_d("oecd", "TABLE_I1", "DEU")
```


## Top Personal Income Tax Rates

```{r PERS-ITAX, echo = T}
ig_d("oecd", "TABLE_I7", "DEU")
```



## Overall Statutory Tax Rates on Dividend

```{r}
ig_d("oecd", "TABLE_II4", "DEU")
```


## Employee Social Contribution Rates

```{r}
ig_d("oecd", "TABLE_III1", "DEU")
```


# Growth in Internal Demand VS External Demand

We decompose the growth in GDP between internal demand and external demand:


```{r}
ig_b("germany", "decompose-internal-external-FRA-GER")
```



# Funded Pensions Indicators (OECD)

## Germany

```{r}
ig_b("germany", "funded-pensions-2")
```


# Inequality

## All population

```{r GINI}
ig_d("oecd", "IDD", "GINI-FRA-DEU")
```


## Age group 76+: mean disposable income (current prices)

```{r INCAC7}
ig_d("oecd", "IDD", "INCAC7-FRA-DEU")
```


## Age group 66-75: mean disposable income (current prices)

```{r INCAC6}
ig_d("oecd", "IDD", "INCAC6-FRA-DEU")
```



## Age group 41-50: mean disposable income (current prices)

```{r INCAC4}
ig_d("oecd", "IDD", "INCAC4-FRA-DEU")
```


## Age group 26-40: mean disposable income (current prices)

```{r INCAC3}
ig_d("oecd", "IDD", "INCAC3-FRA-DEU")
```

##  INCHCTOTAL


```{r INCHCTOTAL}
ig_d("oecd", "IDD", "INCHCTOTAL-FRA-DEU")
```

## P90/P10 disposable income decile ratio

```{r P90P10}
ig_d("oecd", "IDD", "P90P10-FRA-DEU")
```


## P50/P10 disposable income decile ratio

```{r P50P10}
ig_d("oecd", "IDD", "P50P10-FRA-DEU")
```

## P90/P10 disposable income decile ratio

```{r S80S20}
ig_d("oecd", "IDD", "S80S20-FRA-DEU")
```




# Trade surpluses across the world: OECD

Large absolute values of Trade Surpluses:

```{r}
ig_b("germany", "net-exports-QNA")
```



```{r}
ig_b("germany", "net-exports-EO")
```

# Pension Data

```{r}
ig_b("germany", "SOCX_AGG_BRANCH_1")
```

## Old age - Cash benefits

```{r SOCX-AGG-old-cash}
ig_d("oecd", "SOCX_AGG", "old-cash")
```



```{r SOCX-AGG-old-cash2}
ig_d("oecd", "SOCX_AGG", "old-cash2")
```





# Macroeconomic Aggregates

## Total net worth of households

```{r}
ig_d("oecd", "NAAG", "TOTNETWORTHS14-S15NDI-FRA-DEU")
```



## Household housing consumption, percentage of households net adjusted disposable income

```{r}
ig_d("oecd", "NAAG", "P040B7NS14-S15-FRA-DEU")
```

## Household savings (% of household disposable income)

```{r}
ig_d("oecd", "NAAG", "B8NS14-S15SB6NS14-FRA-DEU")
```


# Total Outlays

```{r EO-YPGTQ-FRA-DEU}
ig_d("oecd", "EO", "YPGTQ-FRA-DEU")
```



# Reduced Social Expenditures

## Old age - Cash benefits

```{r}
ig_d("oecd", "SOCX_AGG", "old-cash3")
```



## Total - Cash Benefits

```{r}
ig_d("oecd", "SOCX_AGG", "total-cash-DEU-FRA")
```


## Health - Total

```{r}
ig_d("oecd", "SOCX_AGG", "health-DEU-FRA")
```


## Family - Total

```{r}
ig_d("oecd", "SOCX_AGG", "family-DEU-FRA")
```

## Housing - Total

```{r}
ig_d("oecd", "SOCX_AGG", "housing-DEU-FRA")
```


## Unemployment - Cash Benefits 

```{r SOCX-AGG-unemployment-cash}
ig_d("oecd", "SOCX_AGG", "BRANCH-7-FRA-DEU-NLD")
```

## Old age - Cash benefits

```{r SOCX-AGG-old-cash3}
ig_d("oecd", "SOCX_AGG", "old-cash3")
```



```{r PAG-public-expenditure-pensions}
ig_d("oecd", "PAG", "PEN25-FRA-DEU")
```


```{r PAG-gross-pension-replacement}
ig_d("oecd", "PAG", "PEN3B-FRA-DEU")
```





```{r PAG-PEN5B}
ig_d("oecd", "PAG", "PEN5B-FRA-DEU-1990")
```



```{r PAG-PEN10}
ig_d("oecd", "PAG", "PEN10B-FRA-DEU-1990")
```

# Germany



## Total Taxes (in Billions)

(ref:DEU-TOTALTAX-95-04) <span style="font-variant:small-caps;">Total Taxes in Germany (1995-2004)</span>

```{r DEU-TOTALTAX-95-04, fig.cap="(ref:DEU-TOTALTAX-95-04)"}
ig_d("oecd", "REV", "DEU-TOTALTAX-95-04")
```

## Value Added Taxes (in Billions)

(ref:DEU-5111-95-04) <span style="font-variant:small-caps;">Value Added Taxes in Germany (1995-2004)</span>

```{r DEU-5111-95-04, fig.cap="(ref:DEU-5111-95-04)"}
ig_d("oecd", "REV", "DEU-5111-95-04")
```




## Fuel Taxes (in Billions)

(ref:DEU-5120-95-04) <span style="font-variant:small-caps;">Fuel Taxes in Germany (1995-2004)</span>

```{r DEU-5120-95-04, fig.cap="(ref:DEU-5120-95-04)"}
ig_d("oecd", "REV", "DEU-5120-95-04")
```


# Macroeconomic Aggregates


## Exports and Imports in Germany

(ref:DEU-X-M-95-04) <span style="font-variant:small-caps;">Exports and Imports in Germany (1995-2004)</span>

```{r DEU-X-M-95-04, fig.cap="(ref:DEU-X-M-95-04)"}
ig_d("oecd", "QNA", "DEU-X-M-95-04")
```


## Net Exports

```{r}
ig_d("oecd", "QNA_EXPENDITURE_NATIO_CURR", "P6-P7-B1GQ-DEU")
```





