---
title: Housing Market Insights
metadata-files: 
  - _common.yml
---

```{r, echo = FALSE, message = FALSE}
source(here::here("_rinit.R"))
invisible(Sys.setlocale("LC_TIME", "en_US.UTF-8"))
invisible(Sys.setenv(TZ = "America/Los_Angeles"))
# (was: housing <- tribble(~source, ~dataset, ...) -- now auto: theme_source_datasets("housing"))
```


# Construction

```{r, echo = F}
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R nasq_10_ki; /usr/local/bin/R -e 'quarto::quarto_render("nasq_10_ki.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## Gross investment rate of households

```{r}
ig_d("eurostat", "nasq_10_ki", "IRGS14S15-FR-DE-EA20-2015")
```



# Implicit/imputed rents

```{r, echo = F}
# ?locales
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R hbs_str_t223; /usr/local/bin/R -e 'quarto::quarto_render("hbs_str_t223.qmd")'
# cd ~/iCloud/website/data/oecd; /usr/local/bin/Rscript --vanilla _download_data.R SNA_TABLE5; /usr/local/bin/R -e 'quarto::quarto_render("SNA_TABLE5.qmd")'
# cd ~/iCloud/website/data/oecd; /usr/local/bin/Rscript --vanilla _download_data.R HOUSING; /usr/local/bin/R -e 'quarto::quarto_render("HOUSING.qmd")'
# sh ~/iCloud/website/website_short.sh
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R prc_hicp_midx; /usr/local/bin/R -e 'quarto::quarto_render("prc_hicp_midx.qmd")'
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R nama_10_co3_p3; /usr/local/bin/R -e 'quarto::quarto_render("nama_10_co3_p3.qmd")'
# sh ~/iCloud/website/website_short.sh
```


## By quintile

```{r}
ig_d("eurostat", "hbs_str_t223", "CP041-CP042-CP041042-DE-FR-IT-2015")
```

## Rents as % of Consumption

```{r}
ig_d("oecd", "SNA_TABLE5", "P31CP041-P31CP042-DEU-FRA-USA")
```

## Price Index

```{r}
ig_d("oecd", "HOUSING", "CP040200-FRA-USA-DEU-JPN")
```


## Quintile

```{r}
ig_d("eurostat", "hbs_str_t223", "CP041-CP042-DE-FR-IT-2015")
```


## Actual + imputed rentals

```{r}
ig_d("eurostat", "nama_10_co3_p3", "table1")
```










# Nominal House prices

```{r, echo = F}
# cd ~/iCloud/website/data/bis; /usr/local/bin/R -f SELECTED_PP.R; /usr/local/bin/R -e 'quarto::quarto_render("SELECTED_PP.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## Since 2007 financial crisis

```{r}
ig_d("bis", "SELECTED_PP", "N-DEU-FRA-USA-EA-2007")
```



## Germany, France, Italy, Spain, Netherlands

### 2000-

```{r}
ig_d("bis", "SELECTED_PP", "N-DEU-FRA-ITA-ESP-NLD-2000")
```


# Real House Prices, World

```{r, echo = F}
# cd ~/iCloud/website/data/bis; /usr/local/bin/R -f SELECTED_PP.R; /usr/local/bin/R -e 'quarto::quarto_render("SELECTED_PP.qmd")'
# sh ~/iCloud/website/website_short.sh
```


## Eurostat

```{r}
ig_d("eurostat", "prc_hpi_ooq", "TOTAL-FR-IT-DE")
```


## Japan, South Korea, US

```{r}
ig_d("bis", "SELECTED_PP", "R-JPN-KOR-USA-1975")
```

## France, Germany, E.U., U.S.

```{r}
ig_d("bis", "SELECTED_PP", "R-DEU-FRA-USA-EA")
```




## France, Germany, E.U., U.S.

```{r}
ig_d("bis", "SELECTED_PP", "R-DEU-FRA-USA-EA-1990")
```

## France, Italy, Germany

```{r}
ig_d("bis", "SELECTED_PP", "R-DEU-FRA-ITA-1998")
```


## France, Italy, Germany, Spain, Netherlands

### All

```{r}
ig_d("bis", "SELECTED_PP", "R-DEU-FRA-ITA-ESP-NLD-1990")
```


### 2000-

```{r}
ig_d("bis", "SELECTED_PP", "N-DEU-FRA-ITA-ESP-NLD-2000")
```




## France, Italy, Germany, Spain, Netherlands

```{r}
ig_d("bis", "SELECTED_PP", "N-DEU-FRA-ITA-ESP-NLD-1990")
```


# Household Debt

```{r, echo = F}
# cd ~/iCloud/website/data/bdf; /usr/local/bin/Rscript --vanilla _download_one.R CFT; /usr/local/bin/R -e 'quarto::quarto_render("CFT.qmd")'
# cd ~/iCloud/website/data/bdf; /usr/local/bin/Rscript --vanilla _metadata_one.R CFT
# sh ~/iCloud/website/website_short.sh
```

## 2005-

```{r}
ig_d("bdf", "CFT", "DETT-S1M-FR-IT-DE-ES-JP-EU")
```

## Housing index


```{r}
ig_b("eurostat", "prc_hpi_ooinw_ex2")
```

# Europe

## 2005-

```{r}
ig_d("eurostat", "prc_hpi_q", "TOTAL-EL-FR-ES-IT-DE")
```


# United States

```{r, echo = F}
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -f "housing.R"; /usr/local/bin/R -e 'quarto::quarto_render("housing.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## S&P/Case-Shiller

```{r}
ig_d("fred", "housing", "CPIAUCSL-CSUSHPINSA-index")
```

## Price of Houses

```{r}
ig_d("fred", "housing", "CPIAUCSL-MSPUS-index-2000")
```


## Regions

```{r}
ig_d("fhfa", "index", "los-angeles-las-vegas-denver")
```


# Rents

```{r, echo = F}
# ?locales
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R prc_hicp_midx; /usr/local/bin/R -e 'quarto::quarto_render("prc_hicp_midx.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## France, Germany, Italy

```{r}
ig_d("eurostat", "prc_hicp_midx", "CP041-FR-DE-EL-PT")
```


# Datasets

```{r, echo = F}
theme_source_datasets("housing") |>
  source_dataset_file_updates()
```

# Bibliography

## English

{{< include ../working-papers/en/Geerolf2020.qmd >}}

{{< include ../working-papers/en/Geerolf2015.qmd >}}

## French

{{< include ../publications/fr/Geerolf2023c.qmd >}}

{{< include ../publications/fr/Geerolf2022.qmd >}}

{{< include ../publications/fr/Geerolf2021b.qmd >}}

{{< include ../publications/fr/Geerolf2021a.qmd >}}


