---
title: List of Datasets - Data
subtitle: Data
lang: en
author:
  - name: François Geerolf
    url: https://fgeerolf.com
format:
  html:
    code-fold: false
    toc: true
    theme: flatly
    embed-resources: false
editor: source
---


```{r, echo = FALSE, message = FALSE}
source(here::here("_rinit.R"))
invisible(Sys.setlocale("LC_TIME", "en_US.UTF-8"))
invisible(Sys.setenv(TZ = "America/Los_Angeles"))


# main_datasets -------

main_datasets <- tibble(id = c("ameco",
                               "bea",
                               "bis",
                               "bls",
                               "boe",
                               "buba",
                               "cbp",
                               "census",
                               "comtrade",
                               "crosswalks",
                               "dallas-fed",
                               "destatis",
                               "ec",
                               "ecb",
                               "eurostat",
                               "fhfa",
                               "frb",
                               "frb-ny",
                               "freddie",
                               "gfd",
                               "ilo",
                               "imf",
                               "investing",
                               "john-fernald-tfp",
                               "maddison",
                               "oecd",
                               "ons",
                               "pwt",
                               "statjp",
                               "uk",
                               "un",
                               "us",
                               "wb",
                               "wdi",
                               "wid",
                               "yahoo",
                               "zillow"),
                        label = c("Annual Macro-Economic database of the European COmmission - AMECO",
                                  "Bureau of Economic Analysis - BEA",
                                  "Bureau of International Settlements - BIS",
                                  "Bureau of Labor Statistics - BLS",
                                  "Bank of England - BOE",
                                  "Bundesbank - BUBA",
                                  "County Business Patterns - CBP",
                                  "Census Bureau - census",
                                  "UN Comtrade Database - comtrade",
                                  "Crosswalks",
                                  "Federal Reserve Bank of Dallas - Dallas Fed",
                                  "Statistisches Bundesamt - destatis",
                                  "European Commission - EC",
                                  "European Central Bank - ECB",
                                  "European Statistical Office - Eurostat",
                                  "Federal Housing Finance Agency - fhfa",
                                  "Federal Reserve Board - FRB",
                                  "Federal Reserve Bank of New York - frb-ny",
                                  "Freddie Mac House Price Index - Freddie",
                                  "Global Financial Data - GFD",
                                  "International Labour Organization - ILO",
                                  "International Monetary Fund - IMF",
                                  "Financial Data from investing.com - investing",
                                  "John Fernald TFP - john-fernard-tfp",
                                  "Maddison Data - maddison",
                                  "Organization of Economic Cooperation and Development - OECD",
                                  "Office for National Statisics - ONS",
                                  "Penn World Tables - PWT",
                                  "Statistics Japan, Statistics Bureau, Ministry of Internal Affairs and Communication - statjp",
                                  "Other U.K. Data - uk",
                                  "United Nations - UN",
                                  "Other U.S. Data - us",
                                  "World Bank - WB",
                                  "World Development Indicators - WDI",
                                  "World Income Database - WID",
                                  "Yahoo! Finance - yahoo",
                                  "Housing Data - Zillow Research - zillow"))


# api -------

api <- tibble(id = c("bea",
                     "compustat",
                     "crsp",
                     "dbnomics",
                     "ecb",
                     "imf",
                     "insee",
                     "oecd",
                     "wrds"),
              label =c("Bureau of Economic Analysis Datasets - BEA",
                       "Compustat - compustat",
                       "Center for Research for Security Prices - crsp",
                       "DBnomics - The World's Economic Database - dbnomics",
                       "European Central Bank - ECB",
                       "International Monetary Fund - IMF",
                       "Institut National de la Statistique et des Etudes Economiques - INSEE",
                       "Organization of Economic Cooperation and Development - OECD",
                       "Wharton Research Data Services - WRDS"))

# france -------

france <- tibble(id = c("acoss",
                        "acpr",
                        "bdf",
                        "cepii",
                        "citepa",
                        "cre",
                        "dares",
                        "douanes",
                        "drees",
                        "dvf",
                        "france",
                        "immobilier",
                        "ined",
                        "insee",
                        "ipp",
                        "meteo",
                        "mtes",
                        "olap",
                        "rei",
                        "sdes"),
                 label = c("Agence centrale des organismes de sécurité sociale - ACOSS",
                           "Autorité de Contrôle Prudentiel et de Résolution - ACPR",
                           "Banque de France - BDF",
                           "Centre d’Etudes Prospectives et d’Informations Internationales - CEPII",
                           "Centre technique de référence en matière de pollution atmosphérique et de changement climatique - citepa",
                           "Commission de Régulation de l’Energie - CRE",
                           "Direction de l'Animation de la recherche, des Études et des Statistiques (Ministère du Travail) - DARES",
                           "Douanes - douanes",
                           "Direction de la recherche, des études, de l'évaluation et des statistiques (Ministère de la Santé) - DREES",
                           "Déclarations de Valeurs Foncières - DVF",
                           "France - france",
                           "Données Immobilières, France - Immobilier",
                           "Institut National d'Etudes Démographiques - INED",
                           "Institut National de la Statistique et des Etudes Economiques - INSEE",
                           "Institut des Politiques Publiques - IPP",
                           "Données météorologiques",
                           "Ministère de la Transition Ecologique et Solidaire - MTES",
                           "Observatoire des Loyers de l’Agglomération Parisienne - OLAP",
                           "Relevé des Elements d'Imposition - REI",
                           "Service des Données et des Etudes Statistiques - SDES"))

# databanks -------

databanks <- tibble(id = c("fred",
                           "quandl",
                           "rdb"),
                    label = c("Federal Reserve bank of Saint Louis - fred",
                              "Quandl - Financial, Economic and Alternative Data",
                              "DBnomics - The World's Economic Database - rdb"))


# us_geographies -------

us_geographies <- tibble(id = c("cbsa",
                                "country",
                                "county",
                                "date",
                                "state",
                                "zipcode"),
                         label = c("CBSA Level Datasets (U.S.)",
                                   "Cross-Country Datasets",
                                   "County Level Datasets (U.S.)",
                                   "Time Series Datasets",
                                   "State Level Datasets (U.S.)",
                                   "Zipcode Level Datasets (U.S.)"))

# microeconomic_datasets -------

microeconomic_datasets <- tibble(id = c("compustat",
                                        "crsp"),
                                 label = c("Compustat - compustat",
                                           "Center for Research for Security Prices - crsp"))


themes <- list.files(pattern = "\\.qmd$") %>%
  as_tibble() %>%
  rename(theme = value) %>%
  mutate(theme = gsub("\\.qmd$", "", theme)) %>%
  filter(theme != "api", theme != "index", theme != "themes", !grepl("_update", theme))
```

I created this website for our [2nd year PhD class](https://fgeerolf.com/econ221) "Evidence-Based Macroeconomics and Finance", to help you find macroeconomic datasets. You should find the main sources for macroeconomic datasets out there (as well as a selection of series in each), but this list is by no means not exhaustive. You may find more available at the [UCLA Rosenfeld Library dictionary of databases](https://www.anderson.ucla.edu/rosenfeld-library/databases/business-databases-by-name).


# [Themes](https://fgeerolf.com/data/themes.html)

## Javascript

### English

```{r, echo = FALSE}
themes %>%
  mutate(Title = read_lines(paste0(theme, ".qmd"), skip = 1, n_max = 1) %>% gsub("title: ", "", .) %>% gsub("\"", "", .)) %>%
  mutate(Compile = as.Date(file.info(paste0(theme, ".html"))$mtime),
         Compile = glue::glue("[{Compile}](https://fgeerolf.com/data/{theme}.html)")) %>%
  filter(textcat(Title) == "english") %>%
  gt::gt() |>
  gt::fmt_markdown(columns = "Compile") |>
  gt::opt_interactive(
    use_search = T,
    use_resizers = T,
    use_compact_mode = T
  )
```



### Français

```{r, echo = FALSE}
themes %>%
  mutate(Title = read_lines(paste0(theme, ".qmd"), skip = 1, n_max = 1) %>% gsub("title: ", "", .) %>% gsub("\"", "", .)) %>%
  mutate(Compile = as.Date(file.info(paste0(theme, ".html"))$mtime),
         Compile = glue::glue("[{Compile}](https://fgeerolf.com/data/{theme}.html)")) %>%
  filter(textcat(Title) == "french") %>%
  gt::gt() |>
  gt::fmt_markdown(columns = "Compile") |>
  gt::opt_interactive(
    use_search = T,
    use_resizers = T,
    use_compact_mode = T
  )
```


### Other

```{r, echo = FALSE}
themes %>%
  mutate(Title = read_lines(paste0(theme, ".qmd"), skip = 1, n_max = 1) %>% gsub("title: ", "", .) %>% gsub("\"", "", .)) %>%
  mutate(Compile = as.Date(file.info(paste0(theme, ".html"))$mtime),
         Compile = glue::glue("[{Compile}](https://fgeerolf.com/data/{theme}.html)")) %>%
  filter(!(textcat(Title) %in% c("french", "english"))) %>%
  gt::gt()|>
  gt::fmt_markdown(columns = "Compile") |>
  gt::opt_interactive(
    use_search = T,
    use_resizers = T,
    use_compact_mode = T
  )
```

## Flat

```{r, echo = FALSE}
themes %>%
  mutate(Title = read_lines(paste0(theme, ".qmd"), skip = 1, n_max = 1) %>% gsub("title: ", "", .) %>% gsub("\"", "", .)) %>%
  mutate(Compile = as.Date(file.info(paste0(theme, ".html"))$mtime),
         Compile = glue::glue("[{Compile}](https://fgeerolf.com/data/{theme}.html)")) %>%
  gt::gt() |>
  gt::fmt_markdown(columns = "Compile")
```

# Main Datasets

- Update.qmd. [html](https://fgeerolf.com/data/_update.qmd.html)

- Link. [html](https://fgeerolf.com/data/main.html)

## Javascript

```{r, echo = FALSE}
main_datasets %>%
  gt::gt()  |>
  gt::opt_interactive(
    use_search = T,
    use_resizers = T,
    use_compact_mode = T
  )
```

## Flat

```{r, echo = FALSE}
main_datasets %>%
  gt::gt()
```




# WRDS - Microeconomic Data

Probably the greatest resource for macro / finance data is provided through Wharton Research Data Services. It includes for example Compustat, CRSP, BlockHolders, TRACE, ExecuComp, I/B/E/S, Markit, and many more... All these resources are available through APIs. I provide only some examples below.



## Javascript

```{r, echo = FALSE}
microeconomic_datasets %>%
  mutate(`.html` = as.Date(file.info(paste0(id, "/index.html"))$mtime),
         `.html` = glue::glue("[{.html}](https://fgeerolf.com/data/{id}/index.html)")) %>%
  gt::gt()|>
  gt::fmt_markdown(columns = ".html")|>
  gt::opt_interactive(
    use_search = T,
    use_resizers = T,
    use_compact_mode = T
  )
```

## Flat

```{r, echo = FALSE}
microeconomic_datasets %>%
  mutate(`.html` = as.Date(file.info(paste0(id, "/index.html"))$mtime),
         `.html` = glue::glue("[{.html}](https://fgeerolf.com/data/{id}/index.html)")) %>%
  gt::gt()|>
  gt::fmt_markdown(columns = ".html")
```





# Databanks

## Javascript

```{r, echo = FALSE}
databanks %>%
  gt::gt()|>
  gt::opt_interactive(
    use_search = T,
    use_resizers = T,
    use_compact_mode = T
  )
```

## Flat

```{r, echo = FALSE}
databanks %>%
  gt::gt()
```





# France


## Javascript

```{r, echo = FALSE}
france %>%
  gt::gt()|>
  gt::opt_interactive(
    use_search = T,
    use_resizers = T,
    use_compact_mode = T
  )
```

## Flat

```{r, echo = FALSE}
france %>%
  gt::gt()
```



# All Datasets

## Javascript

```{r, echo = FALSE}
main_datasets %>%
  bind_rows(microeconomic_datasets) %>%
  bind_rows(databanks) %>%
  bind_rows(france) %>%
  add_row(id = "flags", label = "Flag Colors - flags") %>%
  arrange(id) %>%
  gt::gt()|>
  gt::opt_interactive(
    use_search = T,
    use_resizers = T,
    use_compact_mode = T
  )
```

## Flat

```{r, echo = FALSE}
main_datasets %>%
  bind_rows(microeconomic_datasets) %>%
  bind_rows(databanks) %>%
  bind_rows(france) %>%
  add_row(id = "flags", label = "Flag Colors - flags") %>%
  arrange(id) %>%
  gt::gt()
```


# APIs - Application Programming Interfaces

- Link. [html](https://fgeerolf.com/data/api.html)

## List

```{r, echo = FALSE}
api %>%
  gt::gt()
```

## `getSDMXServiceProviders`

An Application Programming Interface (API) is an interface or communication protocol between different parts of a computer program intended to simplify the implementation and maintenance of software. Nowadays, many institutionally provided database are available through APIs. Below, I introduce you to some of these APIs, but there are actually many more you can use. 

We will use the ``rsdmx`` package to read in SDMX data into R statistics:

- `rsdmx` quickstart guide. [html](https://cran.r-project.org/web/packages/rsdmx/vignettes/quickstart.html)

You can easily get a list of providers through `getSDMXServiceProviders`:

```{r, echo = FALSE}
rsdmx::getSDMXServiceProviders() %>%
  as.data.frame %>%
  select(agencyId, name) %>%
  gt::gt()
```


<!---
# Other Datasets

- **Chinn-Ito Openness Index**. [R](kaopen.R)
- **Comtrade**. [API](../api/comtrade.html)
- **NBER Macro History Database**. [R](pwt.R) / [Info](http://www.nber.org/databases/macrohistory/contents/)
- **Political Database (DPI)**. [R](dpi.R)

- **BEA State Level.** [R](bea/bea-regional.R) / [List](bea/index.html) / [BEA Website](https://apps.bea.gov/regional/downloadzip.cfm)
- **CBP**. [R](cbp.R)
- **Census**. [R](census.R) / [html](census.html)
- **Census-STC**. [R](census-stc.R)
- **Crosswalks**. [R](crosswalks.R)
- **Elasticities**. [R](elasticity.R)
- **FRB-NY**. [R](frb-ny/frb-ny.R)
- **IRS**. [R](irs.R) / [R-pre-2010](irs-pre-2010.R) / [Info](https://www.irs.gov/statistics/soi-tax-stats-county-data)
- **Fernald TFP**. [R](us/fernald_2013_data.R)

--->


