---
title: Industry Data Overview
subtitle: Data
author:
  - name: François Geerolf
    url: https://fgeerolf.com
format:
  html:
    code-fold: false
    toc: true
    theme: flatly
    embed-resources: false
editor: source
---


```{r, echo = FALSE, message = FALSE}
source(here::here("_rinit.R"))
invisible(Sys.setlocale("LC_TIME", "en_US.UTF-8"))
invisible(Sys.setenv(TZ = "America/Los_Angeles"))
industry <- tribble(
  ~source, ~dataset,
  "ec", "INDUSTRY",
  "eurostat", "nama_10_a64",
  "eurostat", "nama_10_a64_e",
  "eurostat", "namq_10_a10_e",
  "eurostat", "htec_trd_group4",
  "eurostat", "sts_inpr_m",
  "eurostat", "sts_inppd_m",
  "eurostat", "road_eqr_carmot",
  "eurostat", "ei_isin_m",
  "eurostat", "sts_intvnd_m",
  "eurostat", "sts_inpp_m",
  "fred",  "industry",
  "oecd", "ALFS_EMP",
  "oecd",  "MEI_REAL",
  "oecd",  "GBARD_NABS2007",
  "oecd",  "BERD_MA_SOF",
  "oecd", "MSTI_PUB",
  "oecd", "SNA_TABLE4",
  "wdi", "NV.IND.EMPL.KD",
  "wdi", "NV.IND.MANF.ZS",
  "wdi", "NV.IND.MANF.CD",
  "wdi", "NV.IND.TOTL.KD",
  "wdi", "NV.IND.TOTL.ZS",
  "wdi", "SL.IND.EMPL.ZS",
  "wdi", "TX.VAL.MRCH.CD.WT") %>%
  arrange(source, dataset)
```


# Key facts on industrial production

## France vs. EU

```{r}
ig_d("eurostat", "sts_inpr_m", "FR-EU2027-2000")
```



# Percentage of manufacturing in World

```{r, echo = F}
# cd ~/iCloud/website/data/wdi; /usr/local/bin/Rscript --vanilla _dl_one_value.R NV.IND.MANF.CD; /usr/local/bin/R -e 'quarto::quarto_render("NV.IND.MANF.CD.qmd")'
# cd ~/iCloud/website/data/wdi; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## % of World manufacturing

### Germany, France, Italy, United Kingdom, Spain

```{r}
ig_d("wdi", "NV.IND.MANF.CD", "DE-FR-IT-ES-GB")
```

### China, E.U., U.S.

```{r}
ig_d("wdi", "NV.IND.MANF.CD", "US-CN-EU")
```

## Data on R&D (from Eurostat)

```{r}
i_g("data/eurostat/rd_e_gerdtot_files/figure-html/table1.png")
```



# Value added per worker

### US, UK, Spain

```{r}
ig_d("wdi", "NV.IND.EMPL.KD", "US-GB-ES-log")
```

# Industry (Competitive position in industry)

```{r, echo = F}
# cd ~/iCloud/website/data/oecd; /usr/local/bin/Rscript --vanilla _download_data.R SNA_TABLE3
# cd ~/iCloud/website/data/oecd; /usr/local/bin/R -e 'quarto::quarto_render("SNA_TABLE3.qmd")'
# sh ~/iCloud/website/website_short.sh
# cd ~/iCloud/website/data/oecd; /usr/local/bin/Rscript --vanilla _download_data.R ALFS_EMP
# cd ~/iCloud/website/data/oecd; /usr/local/bin/R -e 'quarto::quarto_render("ALFS_EMP.qmd")'
```

## Competitive position according to Eurostat

```{r}
ig_d("ec", "INDUSTRY", "DE-B-competitive")
```


# Employment

```{r, echo = F}
# cd ~/iCloud/website/data/oecd; /usr/local/bin/Rscript --vanilla _download_data.R SNA_TABLE3
# cd ~/iCloud/website/data/oecd; /usr/local/bin/R -e 'quarto::quarto_render("SNA_TABLE3.qmd")'
# cd ~/iCloud/website/data/oecd; /usr/local/bin/Rscript --vanilla _download_data.R ALFS_EMP
# cd ~/iCloud/website/data/oecd; /usr/local/bin/R -e 'quarto::quarto_render("ALFS_EMP.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## OECD


### France, Manufacture

```{r}
ig_d("oecd", "ALFS_EMP", "FRA-manufacturing")
```


### U.K., Manufacture

```{r}
ig_d("oecd", "ALFS_EMP", "GBR-manufacturing")
```




### U.S., Manufacture

```{r}
ig_d("fred", "industry", "MANEMP-presidents")
```


# Production indexes

```{r, echo = F}
# cd ~/iCloud/website/data/oecd; /usr/local/bin/Rscript --vanilla _download_data.R MEI_REAL; /usr/local/bin/R -e 'quarto::quarto_render("MEI_REAL.qmd")'
# sh ~/iCloud/website/website_short.sh
```


## Retail: an idea of consumption ? (since 1997 approximately !)

### 1990-

```{r}
ig_d("oecd", "MEI_REAL", "SLRTTO01-FRA-DEU-ITA-USA-1990")
```


### 1975-

```{r}
ig_d("oecd", "MEI_REAL", "SLRTTO01-FRA-DEU-ITA-USA-1975")
```



## Manufacturing

```{r}
ig_d("oecd", "MEI_REAL", "PRMNTO01-FRA-DEU-ITA-USA-1995")
```

## Manufacturing

```{r}
ig_d("oecd", "MEI_REAL", "PRMNTO01-FRA-DEU-ITA-USA-1998")
```


## Passenger registration

```{r}
ig_d("eurostat", "road_eqr_carmot", "new-registrations")
```



# Balassa-Samuelson

```{r, echo = F}
# cd ~/iCloud/website/data/oecd; /usr/local/bin/Rscript --vanilla _download_data.R MEI_REAL
# cd ~/iCloud/website/data/oecd; /usr/local/bin/Rscript --vanilla _download_one_var.R MEI_REAL
# cd ~/iCloud/website/data/oecd; /usr/local/bin/R -e 'quarto::quarto_render("MEI_REAL.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## China: Development

```{r}
ig_d("wdi", "PA.NUS.PPPC.RF", "CN-FR-DE")
```



## Japan, Switzerland, Germany, South Korea

```{r}
ig_d("wdi", "PA.NUS.PPPC.RF", "JP-DE-CH")
```

## France, Germany, Switzerland (1960-)

```{r}
ig_d("oecd", "SNA_TABLE4", "PPPGDP-EXC-CHE-DEU-FRA")
```

## Saudi Arabia, South Africa, Colombia

```{r}
ig_d("oecd", "SNA_TABLE4", "PPPGDP-EXC-SAU-ZAF-COL")
```



# High Tech Exports

```{r, echo = F}
# cd ~/iCloud/website/data/oecd; /usr/local/bin/Rscript --vanilla _download_data.R MSTI_PUB
# cd ~/iCloud/website/data/oecd; /usr/local/bin/Rscript --vanilla _download_one_var.R MSTI_PUB
# cd ~/iCloud/website/data/oecd; /usr/local/bin/R -e 'quarto::quarto_render("MSTI_PUB.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## China, United States

```{r}
ig_d("oecd", "MSTI_PUB", "TDEAERO-TDECOMP-TDEDRUG-CHN-USA-log")
```


## China, United States, Germany, France

```{r}
ig_d("oecd", "MSTI_PUB", "TDEAERO-TDECOMP-TDEDRUG-CHN-USA-DEU-FRA-log")
```


# Industrial production

```{r, echo = F}
# cd ~/iCloud/website/data/oecd; /usr/local/bin/R -f "DP_LIVE_7.R"
# cd ~/iCloud/website/data/oecd; /usr/local/bin/R -e 'quarto::quarto_render("DP_LIVE.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## Spain, Italy, France, Germany

### All

```{r}
ig_d("oecd", "DP_LIVE", "INDPROD-MFG-ESP-ITA-FRA-DEU")
```

### 1990-

```{r}
ig_d("oecd", "DP_LIVE", "INDPROD-MFG-ESP-ITA-FRA-DEU-1990")
```


## France

```{r}
ig_d("oecd", "DP_LIVE", "INDPROD-FRA-1990")
```

## Germany

```{r}
ig_d("oecd", "DP_LIVE", "INDPROD-DEU-1990")
```


# Industry

```{r, echo = F}
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R nama_10_a64; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## Number of hours worked

```{r}
ig_d("eurostat", "nama_10_a64_e", "number-employees-industry")
```

# Manufacturing Value Added (NACE)

```{r, echo = F}
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R nama_10_a64; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## C

```{r}
ig_d("eurostat", "nama_10_a64", "C-TOTAL-FR-DE-IT-ES")
```

## C10-C12 - Food products

```{r}
ig_d("eurostat", "nama_10_a64", "C10-C12-TOTAL-FR-DE-IT-ES")
```

## C13-C15 - Textiles

```{r}
ig_d("eurostat", "nama_10_a64", "C13-C15-TOTAL-FR-DE-IT-ES")
```

## C16-C18 - Wood, Paper, Printing

```{r}
ig_d("eurostat", "nama_10_a64", "C16-C18-TOTAL-FR-DE-IT-ES")
```

## C29 - Motor vehicles

```{r}
ig_d("eurostat", "nama_10_a64", "C29-TOTAL-FR-DE-IT-ES")
```

## C29_C30 - Motor vehicles and other transport equipment

```{r}
ig_d("eurostat", "nama_10_a64", "C29-C30-TOTAL-FR-DE-IT-ES")
```


## C28 - Machinery and equipment

```{r}
ig_d("eurostat", "nama_10_a64", "C28-TOTAL-FR-DE-IT-ES")
```

# ILO

## Industry

```{r}
ig_d("ilo", "EMP_2IND_NOC_RT_A", "industry-percent-CHE-DEU-FRA-USA")
```

# Eurostat

```{r, echo = F}
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R namq_10_gdp; /usr/local/bin/R -e 'quarto::quarto_render("namq_10_gdp.qmd")'
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R nama_10_gdp; /usr/local/bin/R -e 'quarto::quarto_render("nama_10_gdp.qmd")'
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R nama_10_a64
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
# cd ~/iCloud/website/data/eurostat
# sh ~/iCloud/website/website_short.sh
```

## Net Exports (Quarterly)

```{r}
ig_d("eurostat", "namq_10_gdp", "P6-P7-NSA-FR-DE-EA")
```



## Net Exports (Annual)

```{r}
ig_d("eurostat", "nama_10_gdp", "P6-P7-NSA-FR-DE-EA")
```


## Manufacturing

```{r}
ig_d("eurostat", "nama_10_a64", "C-TOTAL-FR-DE-IT")
```

## Manufacturing C

```{r}
ig_d("eurostat", "nama_10_a64", "manufacturing-value-added-1995-2019")
```

## All countries


# OECD - QNA

## Germany, Italy, France

```{r}
ig_d("oecd", "QNA", "B1GVB-E-CQR-B1-GE-DEU-FRA-ITA-1995")
```





## Germany, Italy, France

```{r}
ig_d("oecd", "QNA_manufacturing", "B1GVC-CQR-B1-GE-DEU-FRA-JPN-CHN-GBR-IND")
```

## Germany, Italy, France

```{r}
ig_d("oecd", "QNA_manufacturing", "B1GVB-E-CQR-B1-GE-DEU-FRA-ITA-1995")
```


# IMF - Direction of Trade - Bilateral Surpluses

```{r, echo = F}
# cd ~/iCloud/website/data/imf; /usr/local/bin/Rscript --vanilla _download_one.R nama_10_a64
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/R -e 'quarto::quarto_render("nama_10_a64.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## Germany Bilateral

```{r}
ig_d("imf", "DOT", "DE-TBG-USD-A-GDP-CN-US-E1-FR")
```

## France Bilateral

```{r}
ig_d("imf", "DOT", "FR-TBG-US-CN-ES-FR-A-GDP")
```



## US Bilateral

```{r}
ig_d("imf", "DOT", "US-TBG-US-CN-ES-FR-A-GDP")
```


## China Bilateral

```{r}
ig_d("imf", "DOT", "CN-TBG-USD-A-GDP-CN-US-E1-FR")
```

# WDI - Industry, value added (including construction) (NV.IND.TOTL.ZS)

```{r, echo = F}
# cd ~/iCloud/website/data/wdi; /usr/local/bin/Rscript --vanilla _dl_one2.R NV.IND.TOTL.ZS
# cd ~/iCloud/website/data/wdi; /usr/local/bin/R -e 'quarto::quarto_render("NV.IND.TOTL.ZS.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## France, Germany, OECD members

```{r}
ig_d("wdi", "NV.IND.TOTL.ZS", "FR-DE-OE")
```


## Italy, Portugal, Spain

```{r}
ig_d("wdi", "NV.IND.TOTL.ZS", "IT-PT-ES")
```

# WDI - Employment (SL.IND.EMPL.ZS)

```{r, echo = F}
# cd ~/iCloud/website/data/wdi; /usr/local/bin/Rscript --vanilla _dl_one2.R SL.IND.EMPL.ZS
# cd ~/iCloud/website/data/wdi; /usr/local/bin/R -e 'quarto::quarto_render("SL.IND.EMPL.ZS.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## Finland, Sweden, France

```{r}
ig_d("wdi", "SL.IND.EMPL.ZS", "FI-SE-FR")
```

## France, Germany, OECD members

```{r}
ig_d("wdi", "SL.IND.EMPL.ZS", "FR-DE-OE")
```



## China, India, France, Germany, Japan

```{r}
ig_d("wdi", "SL.IND.EMPL.ZS", "CN-FR-DE-IN-GB-US")
```

## China, France, Germany

```{r}
ig_d("wdi", "SL.IND.EMPL.ZS", "CN-FR-DE")
```



## Spain, United Kingdom, United States

```{r}
ig_d("wdi", "SL.IND.EMPL.ZS", "US-GB-ES")
```


## Italy, Portugal, Spain

```{r}
ig_d("wdi", "SL.IND.EMPL.ZS", "IT-PT-ES")
```


## Argentina, Chile, Venezuela

```{r}
ig_d("wdi", "SL.IND.EMPL.ZS", "AR-CL-VE")
```


# Value added in Manufacturing (NV.IND.MANF.ZS)

```{r, echo = F}
# cd ~/iCloud/website/data/wdi; /usr/local/bin/Rscript --vanilla _dl_one2.R NV.IND.MANF.ZS
# cd ~/iCloud/website/data/wdi; /usr/local/bin/R -e 'quarto::quarto_render("NV.IND.MANF.ZS.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## France, OECD, UK, US

```{r}
ig_d("wdi", "NV.IND.MANF.ZS", "EU-1W-FR-US-GB-1995-2021")
```



## France, Germany, OECD members, World

```{r}
ig_d("wdi", "NV.IND.MANF.ZS", "EU-1W-FR-DE-US-GB-1995-2021")
```

## France, Germany, OECD members, World

```{r}
ig_d("wdi", "NV.IND.MANF.ZS", "EU-1W-FR-DE")
```

## France, Germany, OECD members

```{r}
ig_d("wdi", "NV.IND.MANF.ZS", "CN-FR-DE-IN-GB-US-JP-1990")
```




## France, Germany, OECD members

```{r}
ig_d("wdi", "NV.IND.MANF.ZS", "FR-DE-OE")
```


## Italy, Portugal, Spain

```{r}
ig_d("wdi", "NV.IND.MANF.ZS", "IT-PT-ES")
```


## Italy, Portugal, Spain, Greece, France

```{r}
ig_d("wdi", "NV.IND.MANF.ZS", "IT-PT-ES-GR-FR-1995")
```

# WDI - Net exports (NE.RSB.GNFS.ZS)

## Sweden

```{r}
ig_d("wdi", "NE.RSB.GNFS.ZS", "SE")
```

## Israel

```{r}
ig_d("wdi", "NE.RSB.GNFS.ZS", "IL")
```

## Germany

```{r}
ig_d("wdi", "NE.RSB.GNFS.ZS", "DE")
```

## Germany, France, Italy

```{r}
ig_d("wdi", "NE.RSB.GNFS.ZS", "DE-FR-IT-flags")
```

## Germany, France, Switzerland

```{r}
ig_d("wdi", "NE.RSB.GNFS.ZS", "DE-FR-CH-flags")
```


# SNA_TABLE6A

## Luxembourg, Cyprus, Australia

```{r}
ig_d("oecd", "SNA_TABLE6A", "LUX-CYP-AUS")
```

## Albania, Norway, Greece

```{r}
ig_d("oecd", "SNA_TABLE6A", "ALB-NOR-GRC")
```

## Malta, Iceland, United Kingdom

```{r}
ig_d("oecd", "SNA_TABLE6A", "MLT-ISL-GBR")
```

## Chile, Canada, France

### All

```{r}
ig_d("oecd", "SNA_TABLE6A", "CHL-CHL-FRA")
```

### 2007-

```{r}
ig_d("oecd", "SNA_TABLE6A", "CHL-CHL-FRA-2007")
```


## New Zealand, Latvia, Brazil

```{r}
ig_d("oecd", "SNA_TABLE6A", "NZL-LVA-BRA")
```


## Netherlands, United States, Costa Rica

```{r}
ig_d("oecd", "SNA_TABLE6A", "NLD-USA-CRI")
```

## Spain, Colombia, Portugal

```{r}
ig_d("oecd", "SNA_TABLE6A", "ESP-COL-PRT")
```



# SNA_TABLE6A_ARCHIVE

## France, Germany, US

```{r}
ig_d("oecd", "SNA_TABLE6A_ARCHIVE", "value-added-manuf-DEU-FRA-USA")
```


## Denmark, Switzerland, UK

```{r}
ig_d("oecd", "SNA_TABLE6A_ARCHIVE", "value-added-manuf-GBR-DNK-CHE")
```


## Spain, Italy, Portugal

```{r}
ig_d("oecd", "SNA_TABLE6A_ARCHIVE", "value-added-manuf-ESP-ITA-PRT")
```


## Finland, Sweden, Norway

```{r}
ig_d("oecd", "SNA_TABLE6A_ARCHIVE", "value-added-manuf-FIN-SWE-NOR")
```


## Denmark, Switzerland, UK

```{r}
ig_d("oecd", "SNA_TABLE6A_ARCHIVE", "value-added-manuf-KOR-NZL-AUS")
```

# Basic Summary Stats on Manufacturing

## 

```{r}
ig_d("oecd", "SNA_TABLE1", "B1GVC-B1-GE-USA-FRA-GBR-flags")
```



# Manufacturing - WDI


## France, Germany, OECD

```{r, out.width = "95%"}
ig_d("wdi", "NV.IND.MANF.ZS", "FR-DE-OE")
```


