---
title: Overview of Inflation Data in Europe
subtitle: Data
lang: en
author:
  - name: François Geerolf
    url: https://fgeerolf.com
format:
  html:
    code-fold: false
    toc: true
    theme: flatly
    embed-resources: false
    include-in-header:
      - text: |
          <link rel="stylesheet" href="https://cdnjs.cloudflare.com/ajax/libs/font-awesome/6.4.0/css/all.min.css">
editor: source
---


```{r, echo = FALSE, message = FALSE}
source(here::here("_rinit.R"))
invisible(Sys.setlocale("LC_TIME", "en_US.UTF-8"))
invisible(Sys.setenv(TZ = "America/Los_Angeles"))
`inflation-europe` <- tribble(
  ~source, ~dataset,
  "ecb", "CES",
  "eurostat",  "prc_hicp_manr",
  "eurostat",  "prc_hicp_midx",
  "eurostat",  "prc_hicp_mmor",
  "eurostat",  "prc_hicp_inw",
  "eurostat",  "prc_hicp_cow",
  "eurostat",  "prc_ppp_ind",
  "eurostat",  "prc_hicp_ctrb",
  "eurostat", "nama_10_co3_p3") %>%
  arrange(source, dataset)
```



# United States vs Europe

## Flavors of inflation

```{r}
ig_d("fred", "inflation", "CPIAUCSL-PCEPI-CP0000USM086NEST-CP00MI15EA20M086NEST-2020")
```

## Flavors of CPI

```{r}
ig_d("fred", "inflation", "CPIAUCSL-PCEPI-CP0000USM086NEST-CP00MI15EA20M086NEST-2020-index")
```


## Decomposition

```{r}
ig_d("oecd", "PRICES_CPI", "EU-US-contributions")
```


## Focus on energy prices

```{r}
ig_d("fred", "energy", "electricity-natural-gas-fuel-2020-facet")
```


## All, Rents

```{r}
ig_d("fred", "housing", "all-rents-HICP-CPI")
```


## Inflation by HICP category

```{r}
ig_d("eurostat", "prc_hicp_manr", "RCH-A-CP00-EA20-US-2020-facet")
```


## CPI by HICP category

```{r}
ig_d("eurostat", "prc_hicp_midx", "I15-2-digit-EA20-US-2020-facet")
```


## Heterogeneity

```{r}
ig_d("eurostat", "prc_hicp_midx", "CP00-TOT-X-NRG-FOOD-standard-deviation-weighted-1-2-years")
```





# France, Germany, Italy, Spain, Europe

```{r, echo = F}
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R prc_hicp_manr; /usr/local/bin/R -e 'quarto::quarto_render("prc_hicp_manr.qmd")'
# sh ~/iCloud/website/website_short.sh
```


## All

```{r}
ig_d("eurostat", "prc_hicp_manr", "RCH-A-CP00-FR-DE-ES-IT-EA19-2020")
```



## All

```{r}
ig_d("eurostat", "prc_hicp_manr", "RCH-A-CP00-FR-DE-ES-IT-EA19-US-2Y")
```





## Core inflation

```{r}
ig_d("eurostat", "prc_hicp_manr", "TOT-X-NRG-FOOD-FR-DE-ES-IT-2020")
```


## Rents

```{r}
ig_d("eurostat", "prc_hicp_manr", "RCH-A-CP041-FR-DE-ES-IT-EA19-2020")
```

## Natural gas

```{r}
ig_d("eurostat", "prc_hicp_manr", "RCH-A-CP04521-FR-DE-BE-NL-2Y")
```





# Weights - France

```{r, echo = F}
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R prc_hicp_inw; /usr/local/bin/R -e 'quarto::quarto_render("prc_hicp_inw.qmd")'
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R nama_10_co3_p3; /usr/local/bin/R -e 'quarto::quarto_render("nama_10_co3_p3.qmd")'
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
# cd ~/iCloud/website/data/eurostat
# sh ~/iCloud/website/website_short.sh
```


## Food + Housing + Transport = more than half

### % of Consumption - Weights

```{r}
ig_d("eurostat", "prc_hicp_inw", "FRA-CP01-CP04-CP07")
```

### % of Consumption

```{r}
ig_d("eurostat", "nama_10_co3_p3", "FR-CP04-CP07-CP01-PCTOT")
```

### % of GDP Value

```{r}
ig_d("eurostat", "nama_10_co3_p3", "FR-CP04-CP07-CP01-CPMEUR")
```



# Bibliography


{{< include ../publications/inflation.qmd >}}
