---
title: Insights into Inflation Statistics
subtitle: Data
author:
  - name: François Geerolf
    url: https://fgeerolf.com
format:
  html:
    code-fold: false
    toc: true
    theme: flatly
    embed-resources: false
editor: source
---


```{r, echo = FALSE, message = FALSE}
source(here::here("_rinit.R"))
invisible(Sys.setlocale("LC_TIME", "fr_FR.UTF-8"))
invisible(Sys.setenv(TZ = "Europe/Paris"))
inflation <- tribble(
  ~source, ~dataset,
  "bis",  "CPI",
  "ecb", "CES",
  "eurostat", "nama_10_co3_p3",
  "eurostat",  "prc_hicp_manr",
  "eurostat",  "prc_hicp_midx",
  "eurostat",  "prc_hicp_mmor",
  "eurostat",  "prc_hicp_inw",
  "eurostat",  "prc_hicp_cow",
  "eurostat",  "prc_ppp_ind",
  "eurostat",  "prc_hicp_ctrb",
  "eurostat",  "sts_inpp_m",
  "eurostat",  "sts_inppd_m",
  "eurostat",  "sts_inppnd_m",
  "fred",  "cpi",
  "fred",  "inflation",
  "imf", "CPI",
  "oecd",  "MEI_PRICES_PPI",
  "oecd",  "PRICES_CPI",
  "oecd", "PPP2017",
  "wdi",  "NY.GDP.DEFL.KD.ZG",
  "wdi",  "FP.CPI.TOTL.ZG") %>%
  arrange(source, dataset)
```

# Info

```{r, echo = F}
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("inflation.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("inflation-france.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("xrates.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("themes.qmd")'
# sh ~/iCloud/website/website_short.sh
```

# Related papers

## English

{{< include ../publications/en/Geerolf2024c.qmd >}}

{{< include ../publications/en/Geerolf2024b.qmd >}}

{{< include ../publications/en/Geerolf2024a.qmd >}}

{{< include ../publications/en/Geerolf2023c.qmd >}}

- "Are inflation dynamics different in the euro area and the United States?" C. Blot & F. Geerolf, Monetary Dialogue Paper, November 2023, requested by the ECON committee, European Parliament. [[pdf](https://www.europarl.europa.eu/RegData/etudes/IDAN/2023/755706/IPOL_IDA(2023)755706_EN.pdf)] [[html](https://www.europarl.europa.eu/thinktank/fr/document/IPOL_IDA(2023)755706)]

- "The direct and indirect impacts of the war on inflation." C. Blot, J. Creel & F. Geerolf, Monetary Dialogue Paper, March 2023, requested by the ECON committee, European Parliament. [[pdf](https://www.europarl.europa.eu/RegData/etudes/IDAN/2023/741487/IPOL_IDA(2023)741487_EN.pdf)] [[html](https://www.europarl.europa.eu/thinktank/en/document/IPOL_IDA(2023)741487)]

- "Heterogeneity of inflation in the euro area: more complicated than it seems." C. Blot, J. Creel, F. Geerolf & S. Levasseur, Monetary Dialogue Paper, November 2022, requested by the ECON committee, European Parliament. [[pdf](https://www.europarl.europa.eu/RegData/etudes/IDAN/2022/733999/IPOL_IDA(2022)733999_EN.pdf)] [[html](https://www.europarl.europa.eu/thinktank/en/document/IPOL_IDA(2022)733999)]

- "Social Impact of the War in Ukraine (SIWU)." F. Geerolf, X. Timbeau & G. Allègre, OFCE Github repo, July 2022. [[html](https://github.com/OFCE/SIWU)]

{{< include ../publications/en/Geerolf2022.qmd >}}

- "The Phillips Curve: a Relation between Real Exchange Rate Growth and Unemployment." F. Geerolf, January 2020. [[pdf](https://fgeerolf.com/phillips.pdf)]

## French

{{< include ../publications/fr/Geerolf2024c.qmd >}}

{{< include ../publications/fr/Geerolf2024b.qmd >}}

{{< include ../publications/fr/Geerolf2024a.qmd >}}

{{< include ../publications/fr/Geerolf2023c.qmd >}}

{{< include ../publications/fr/Geerolf2023b.qmd >}}

- "Une analyse macroéconomique de l'inflation.", C. Antonin & F. Geerolf, In la Jaune et la Rouge n°783, mars 2023. [[pdf](https://www.lajauneetlarouge.com/wp-content/uploads/2023/02/La_Jaune_et_la_Rouge_783_41-44.pdf)] [[html](https://www.lajauneetlarouge.com/analyse-macroeconomique-de-linflation-et-de-la-pertinence-de-nos-modeles/)]

{{< include ../publications/fr/Geerolf2023a.qmd >}}

- "Qui va payer cette facture énergétique ?" F. Geerolf, Interview a priori, décembre 2022. [[html](https://a-prioris.fr/hauteur-de-vue/francois-geerolf-qui-va-payer-cette-facture-energetique)]

- "Inflation en Europe : les conséquences sociales de la guerre en Ukraine." G. Allègre, F. Geerolf, X. Timbeau, Blog de l'OFCE, juillet 2022. [[html](https://www.ofce.sciences-po.fr/blog/inflation-en-europe-les-consequences-sociales-de-la-guerre-en-ukraine/)]

- Inflation et pouvoir d'achat : it's the politics, stupid! F. Geerolf & P. Jacquet, Relançons le débat économique, juin 2022. [[pdf](https://lecercledeseconomistes.fr/wp-content/uploads/2022/07/rlde-2022-25-geerolfjacquet.pdf)] [[html](https://lecercledeseconomistes.fr/inflation-et-pouvoir-dachat-its-the-politics-stupid/)]

{{< include ../publications/fr/Geerolf2022.qmd >}}

- "Le keynésianisme doit-il faire l'économie de la courbe de Phillips ?" F. Geerolf, In L'économie mondiale 2022, La Découverte, p.73-86, septembre 2021. [[pdf](http://www.cepii.fr/PDF_PUB/em/2022/em2022-05.pdf)] [[slides](http://www.cepii.fr/docs/files/reunions/communications/em2022/Economie%20Mondiale%202022_Geerolf.pdf)]

- "La courbe de Phillips n'est pas celle que vous croyez." F. Geerolf, La Lettre du CEPII, n°417, avril 2021. [[pdf](http://www.cepii.fr/PDF_PUB/lettre/2021/let417.pdf)] [[html](http://www.cepii.fr/CEPII/fr/publications/lettre/abstract.asp?NoDoc=12974)]


# Inflation

```{r, echo = F}
# cd ~/iCloud/website/data/oecd; /usr/local/bin/R -f PRICES_CPI_5.R; /usr/local/bin/R -e 'quarto::quarto_render("PRICES_CPI.qmd")'
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -f "inflation.R"; /usr/local/bin/R -e 'quarto::quarto_render("inflation.qmd")'
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -f "cpi.R"; /usr/local/bin/R -e 'quarto::quarto_render("cpi.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## France, Germany, EU, US (OECD)

### 2 years

```{r}
ig_d("oecd", "PRICES_CPI", "CPALTT01-GY-M-FRA-DEU-USA-EA20-2Y")
```



### 1 year

```{r}
ig_d("oecd", "PRICES_CPI", "CPALTT01-GY-M-FRA-DEU-USA-EA20-1Y")
```



## France vs. Germany

### All

```{r}
ig_d("oecd", "PRICES_CPI", "CPALTT01-GY-M-FRA-DEU")
```

### 1 year

```{r}
ig_d("oecd", "PRICES_CPI", "CPHPTT01-CPALTT01-GY-M-FRA-DEU-1Y")
```

## United States

### Importance of shelter

```{r}
ig_d("fred", "inflation", "CPIAUCSL-CUUR0000SA0L2-2-years")
```

# Inflation Expectations

```{r, echo = F}
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -f "energy.R"; /usr/local/bin/R -e 'quarto::quarto_render("energy.qmd")'
# cd ~/iCloud/website/data/ecb; /usr/local/bin/R -f "CES.R"; /usr/local/bin/R -e 'quarto::quarto_render("CES.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## Gas prices and Inflation expectations

### 1990-

```{r}
ig_d("fred", "energy", "GASREGW-MICH-1990")
```

### 1995-

```{r}
ig_d("fred", "energy", "GASREGW-MICH-1995")
```

## Consumer Expenditure Survey

### 1-year

```{r}
ig_d("ecb", "CES", "c1020-mean")
```

### 3-year

```{r}
ig_d("ecb", "CES", "c1220-mean")
```

# Measures of inflation

```{r, echo = F}
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R prc_hicp_midx; /usr/local/bin/R -e 'quarto::quarto_render("prc_hicp_midx.qmd")'
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R prc_hicp_manr; /usr/local/bin/R -e 'quarto::quarto_render("prc_hicp_manr.qmd")'
# cd ~/iCloud/website/data/insee; /usr/local/bin/Rscript --vanilla _download_one.R IPCH-2015; /usr/local/bin/R -e 'quarto::quarto_render("IPCH-2015.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## France VS Insee

```{r}
ig_d("oecd", "PRICES_CPI", "CPALTT01-FRA-USA-DEU-JPN-1996")
```



## Insee

### 1996-

```{r}
ig_d("insee", "IPCH-2015", "IPC-IPCH-00-1996")
```


## GDP Deflator

```{r}
ig_d("eurostat", "namq_10_gdp", "B1GQ-NSA-PD15EUR-FR-DE-1996")
```

## Consumption Deflator

```{r}
ig_d("eurostat", "namq_10_gdp", "P3-NSA-PD15EUR-FR-DE-1996")
```



## OECD

OECD: IPC de l'Insee

```{r}
ig_d("oecd", "PRICES_CPI", "CPALTT01-M-FRA-DEU-1996")
```


## Eurostat

### All

```{r}
ig_d("eurostat", "prc_hicp_midx", "CP00-FR-DE")
```



### 1999-

```{r}
ig_d("eurostat", "prc_hicp_midx", "CP00-FR-DE")
```


# Producer price inflation

```{r, echo = F}
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R sts_inpp_m; /usr/local/bin/R -e 'quarto::quarto_render("sts_inpp_m.qmd")'
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R sts_inppd_m; /usr/local/bin/R -e 'quarto::quarto_render("sts_inppd_m.qmd")'
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R sts_inppnd_m; /usr/local/bin/R -e 'quarto::quarto_render("sts_inppnd_m.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## Manufacturing, All

### All

#### Price Index

```{r}
ig_d("eurostat", "sts_inpp_m", "C-FR-DE-IT-2018")
```

#### % change compared to same period in previous year

```{r}
ig_d("eurostat", "sts_inpp_m", "C-PRON-FR-DE-IT-PCHSM-2018")
```





### Non Domestic

```{r}
ig_d("eurostat", "sts_inppnd_m", "C-FR-DE-IT-2018")
```
