---
title: Data on interest rates
subtitle: Data
lang: en
author:
  - name: François Geerolf
    url: https://fgeerolf.com
format:
  html:
    code-fold: false
    toc: true
    theme: flatly
    embed-resources: false
editor: source
---


```{r, echo = FALSE, message = FALSE}
source(here::here("_rinit.R"))
invisible(Sys.setlocale("LC_TIME", "en_US.UTF-8"))
invisible(Sys.setenv(TZ = "America/Los_Angeles"))
load(here::here("flags", "colors.RData"))
library("gt")
knitr::opts_chunk$set(echo = T)
`interest-rates` <- tribble(
  ~source, ~dataset,
  "bdf",  "FM",
  "bdf",  "MIR",
  "bdf",  "MIR1",
  "bis",  "CBPOL_D",
  "bis",  "CBPOL_M",
  "ecb",  "FM",
  "ecb",  "MIR",
  "eurostat", "ei_mfir_m",
  "eurostat", "irt_st_m",
  "eurostat", "irt_lt_mcby_d",
  "fred",  "r",
  "oecd",  "MEI",
  "oecd",  "MEI_FIN",
  "wdi",  "FR.INR.RINR") %>%
  arrange(source, dataset)
```


# Info

```{r, echo = F}
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("taux-dinteret.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("interest-rates.qmd")'
# sh ~/iCloud/website/website_short.sh
```

# Current rates

## Policy rates

```{r, echo = F}
temp <- "https://www.investing.com/central-banks/" |>
  rvest::read_html() |>
  rvest::html_table(header = T, fill = T) |>
  pluck(1) %>%
  select(-1)

temp |>
  mutate(country_code_2 = case_when(grepl("Federal", `Central Bank`) ~ "US",
                                    grepl("European", `Central Bank`) ~ "EU",
                                    grepl("England", `Central Bank`) ~ "GB",
                                    grepl("Swiss", `Central Bank`) ~ "CH",
                                    grepl("Australia", `Central Bank`) ~ "AU",
                                    grepl("Canada", `Central Bank`) ~ "CA",
                                    grepl("New Zealand", `Central Bank`) ~ "NZ",
                                    grepl("Japan", `Central Bank`) ~ "JP",
                                    grepl("Russia", `Central Bank`) ~ "RU",
                                    grepl("India", `Central Bank`) ~ "IN",
                                    grepl("China", `Central Bank`) ~ "CN",
                                    grepl("Brazil", `Central Bank`) ~ "BR")) |>
  select(country_code_2, everything()) |>
  gt()|>
    tab_options(
      quarto.disable_processing = TRUE
    ) |> 
  fmt_flag(columns = country_code_2) |>
  cols_align(
    align = "center",
    columns = -c(`Central Bank`)) |>
  cols_label(
    country_code_2 = ""
    )|>
  fmt_number(
    dec_mark = ",",
    sep_mark = ".",
    decimals = 2
  ) |>
  opt_interactive(
    use_search = F,
    use_pagination = F,
    use_pagination_info = F,
    use_compact_mode = T,
    page_size_default = 20,
    page_size_values = c(5, 10, 15, 20),
    use_resizers = T,
    use_highlight = T
  # ) |>
  # cols_width(
  #   c("country_code_2") ~ px(40),
  #   c("Current Rate") ~ px(120),
  #   c("Next Meeting") ~ px(140),
  #   c("Central Bank") ~ px(280),
  #   everything() ~ px(200)
  ) |>
  gt::tab_source_note(
    source_note = gt::md(paste0("Date: ", format(Sys.time(), format = "%B %d, %Y %I:%M %p"), ". Source: <https://www.investing.com/central-banks/>"))
  ) |>
  gt::tab_options(table.width = "100%")
```

## Sovereign rates

```{r, echo = F}
temp <- "https://tradingeconomics.com/country-list/rating" |>
  rvest::read_html() |>
  rvest::html_table(header = T, fill = T)

ratings <- temp[[1]] |>
  rename(country = 1)

temp <- "https://www.investing.com/rates-bonds/world-government-bonds" |>
  rvest::read_html() |>
  rvest::html_table(header = T, fill = T)

# length(temp) - 4 car les.4 dernières tibble ne sont pas des données de taux souverains
# on enlève les warnings pour la transformation de Chg. en numeric

taux_souverains <- tibble(num = 1:(length(temp)-4)) %>%
  mutate(data = map(num, ~ temp[[.]] %>%
                      select(2:7) %>%
                      mutate(`Chg.` = suppressWarnings(as.numeric(`Chg.`))))) %>%
  unnest(cols = c(data)) %>%
  select(-num) %>%
  mutate(duration = str_extract(Name, "\\d+[YM]$"),
         country = str_trim(str_extract(Name, "^[\\p{L} .'’]+")),
         country = case_when(country == "U.S." ~ "United States",
                             country == "U.K." ~ "United Kingdom",
                             T ~ country)) %>%
  mutate(country = ifelse(country == "Cote d'Ivoire", "Ivory Coast", country)) %>%
  select(-Name) %>%
  select(country, duration, everything())
```


### 5Y, 10Y, 30Y

```{r, echo = F}
library(countrycode)
country_codes <- codelist |>
  select(country = country.name.en, country_code_2 = genc2c)

taux_souverains %>%
  filter(duration %in% c("5Y", "10Y", "30Y")) %>%
  select(country, duration, Yield) %>%
  spread(duration, Yield) |>
  left_join(country_codes, by = "country") |>
  select(country_code_2, country, `10Y`, `30Y`, everything()) |>
  arrange(`10Y`) |>
  filter(!is.na(country)) |>
  gt()|>
    tab_options(
      quarto.disable_processing = TRUE
    ) |> 
  cols_align(
    align = "center",
    columns = -c(country))|>
  cols_label(
    country = "",
    country_code_2 = ""
    )|>
  fmt_number(
    dec_mark = ",",
    sep_mark = ".",
    decimals = 2
  ) |>
  fmt_flag(columns = country_code_2) |>
  sub_missing(
    missing_text = ""
  )|>
  opt_interactive(
    use_search = F,
    use_pagination = T,
    use_pagination_info = F,
    use_compact_mode = T,
    page_size_default = 20,
    page_size_values = c(20, 30, 50, 100),
    use_resizers = T,
    use_highlight = T
  ) |>
  gt::tab_source_note(
    source_note = gt::md(paste0("Date: ", format(Sys.time(), format = "%B %d, %Y %I:%M %p"), ". Source: <https://www.investing.com/rates-bonds/world-government-bonds>"))
  ) |>
  gt::tab_options(table.width = "100%")
```



### 10Y, 30Y, ratings

```{r, echo = F}
ratings_taux <- taux_souverains %>%
  filter(duration %in% c("10Y", "30Y")) %>%
  select(country, duration, Yield) %>%
  spread(duration, Yield) %>%
  left_join(ratings, by = "country")

country_codes <- codelist |>
  select(country = country.name.en, country_code_2 = genc2c)

ratings_taux |>
  left_join(country_codes, by = "country") |>
  select(-DBRS) |>
  select(country_code_2, country, everything()) |>
  arrange(-TE, `10Y`) |>
  select(-TE) |>
  filter(!is.na(country)) |>
  gt()|>
    tab_options(
      quarto.disable_processing = TRUE
    ) |> 
  cols_align(
    align = "center",
    columns = -c(country))|>
  cols_label(
    country = "",
    country_code_2 = ""
    )|>
  fmt_number(
    dec_mark = ",",
    sep_mark = ".",
    decimals = 2
  ) |>
  fmt_flag(columns = country_code_2) |>
  sub_missing(
    missing_text = ""
  )|>
  opt_interactive(
    use_search = F,
    use_pagination = T,
    use_pagination_info = F,
    use_compact_mode = T,
    page_size_default = 20,
    page_size_values = c(20, 30, 50, 100),
    use_resizers = T,
    use_highlight = T
  ) |>
  gt::tab_source_note(
    source_note = gt::md(paste0("Date: ", format(Sys.time(), format = "%B %d, %Y %I:%M %p"), ". Source: <https://www.investing.com/rates-bonds/world-government-bonds>"))
  ) |>
  gt::tab_options(table.width = "100%")
```


### Yield Curve

#### France, Italy, Spain, Germany

```{r YC-France-Italy-Spain-Germany, echo = F}
taux_souverains %>%
  mutate(number = parse_number(duration),
         number = ifelse(duration %in% paste0(1:12, "M"), number/12, number)) %>%
  filter(country %in% c("France", "Italy", "Spain", "Germany")) %>%
  left_join(colors, by = "country") %>%
   ggplot + geom_line(aes(x = number, y = Yield/100, color = color)) +
  scale_color_identity() + 
  theme_minimal() + xlab("Maturity") + ylab("Par yield curve rate") +
  scale_x_log10(breaks = c(1/12, 3/12, 6/12, 9/12, 1, 2, 5, 10, 15, 20, 30, 50),
                     labels = c("1M", "3M", "6M", "9M", "1Y", "2Y", "5Y", "10Y", "15Y", "20Y", "30Y", "50Y")) +
  scale_y_continuous(breaks = 0.01*seq(-10, 50, 0.2),
                     labels = scales::percent_format(accuracy = .1)) +
  theme(legend.position = c(0.2, 0.8),
        legend.title = element_blank()) +
  ggimage::geom_image(data = . %>% group_by(number) %>%
                           filter(n() == 4) %>%
                           arrange(Yield) %>%
                           mutate(dist = min(Yield[2]-Yield[1],Yield[3]-Yield[2],Yield[4]-Yield[3])) %>%
                           arrange(-dist, Yield) %>%
                           head(4) %>%
                           mutate(image = paste0("../icon/flag/round/", str_to_lower(gsub(" ", "-", country)), ".png")),
                         aes(x = number, y = Yield/100, image = image), asp = 1.5)
```


#### France, Germany, US, Greece

```{r YC-France-Germany-US-Greece, echo = F}
taux_souverains %>%
  mutate(number = parse_number(duration),
         number = ifelse(duration %in% paste0(1:12, "M"), number/12, number)) %>%
  filter(country %in% c("France", "United States", "Germany", "Greece")) %>%
  left_join(colors, by = "country") %>%
   ggplot + geom_line(aes(x = number, y = Yield/100, color = color)) +
  scale_color_identity() + 
  theme_minimal() + xlab("Maturity") + ylab("Par yield curve rate") +
  scale_x_log10(breaks = c(1/12, 3/12, 6/12, 9/12, 1, 2, 5, 10, 15, 20, 30, 50),
                     labels = c("1M", "3M", "6M", "9M", "1Y", "2Y", "5Y", "10Y", "15Y", "20Y", "30Y", "50Y")) +
  scale_y_continuous(breaks = 0.01*seq(-10, 50, 0.2),
                     labels = scales::percent_format(accuracy = .1)) +
  theme(legend.position = c(0.2, 0.8),
        legend.title = element_blank()) +
  ggimage::geom_image(data = . %>% group_by(number) %>%
                           filter(n() == 4) %>%
                           arrange(Yield) %>%
                           mutate(dist = min(Yield[2]-Yield[1],Yield[3]-Yield[2],Yield[4]-Yield[3])) %>%
                           arrange(-dist, Yield) %>%
                           head(4) %>%
                           mutate(image = paste0("../icon/flag/round/", str_to_lower(gsub(" ", "-", country)), ".png")),
                         aes(x = number, y = Yield/100, image = image), asp = 1.5)
```


#### France, US, UK, Canada

```{r YC-France-Germany-UK-Australia, echo = F}
taux_souverains %>%
  mutate(number = parse_number(duration),
         number = ifelse(duration %in% paste0(1:12, "M"), number/12, number)) %>%
  filter(country %in% c("France", "United States", "United Kingdom", "Australia")) %>%
  left_join(colors, by = "country") %>%
   ggplot + geom_line(aes(x = number, y = Yield/100, color = color)) +
  scale_color_identity() + 
  theme_minimal() + xlab("Maturity") + ylab("Par yield curve rate") +
  scale_x_log10(breaks = c(1/12, 3/12, 6/12, 9/12, 1, 2, 5, 10, 15, 20, 30, 50),
                     labels = c("1M", "3M", "6M", "9M", "1Y", "2Y", "5Y", "10Y", "15Y", "20Y", "30Y", "50Y")) +
  scale_y_continuous(breaks = 0.01*seq(-10, 50, 0.2),
                     labels = scales::percent_format(accuracy = .1)) +
  theme(legend.position = c(0.2, 0.8),
        legend.title = element_blank()) +
  ggimage::geom_image(data = . %>% group_by(number) %>%
                           filter(n() == 4) %>%
                           arrange(Yield) %>%
                           mutate(dist = min(Yield[2]-Yield[1],Yield[3]-Yield[2],Yield[4]-Yield[3])) %>%
                           arrange(-dist, Yield) %>%
                           head(4) %>%
                           mutate(image = paste0("../icon/flag/round/", str_to_lower(gsub(" ", "-", country)), ".png")),
                         aes(x = number, y = Yield/100, image = image), asp = 1.5)
```




# Long-term rates

```{r, echo = F}
# cd ~/iCloud/website/data/bdf; /usr/local/bin/R -f "FM.R"; /usr/local/bin/R -e 'quarto::quarto_render("FM.qmd")'
## cd ~/iCloud/website/data/oecd; /usr/local/bin/R -f MEI_16.R; /usr/local/bin/R -e 'quarto::quarto_render("MEI.qmd")'
## cd ~/iCloud/website/data/oecd; /usr/local/bin/Rscript --vanilla _download_data.R MEI_FIN; /usr/local/bin/R -e 'quarto::quarto_render("MEI_FIN.qmd")'
# sh ~/iCloud/website/website_short.sh
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -f "r.R"; /usr/local/bin/R -e 'quarto::quarto_render("r.qmd")'
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R ei_mfir_m; /usr/local/bin/R -e 'quarto::quarto_render("ei_mfir_m.qmd")'
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R irt_lt_mcby_d; /usr/local/bin/R -e 'quarto::quarto_render("irt_lt_mcby_d.qmd")'
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
# cd ~/iCloud/website/data/oecd; /usr/local/bin/R -e 'quarto::quarto_render("api.qmd")'
# sh ~/iCloud/website/website_short.sh
```



## France, Germany, Greece, Spain, Italy

### 2020-

```{r}
ig_d("eurostat", "irt_lt_mcby_d", "FR-DE-IT-ES-EL-2020")
```

### 3 months

```{r}
ig_d("eurostat", "irt_lt_mcby_d", "FR-DE-IT-ES-EL-last-3-months")
```


### 1 month

```{r}
ig_d("eurostat", "irt_lt_mcby_d", "FR-DE-IT-ES-EL-last-1-month")
```



## U.S., France, Japan, Germany

### MEI

```{r}
ig_d("oecd", "MEI", "IRLTLT01-FRA-USA-DEU-JPN-2010")
```


### MEI_FIN

```{r}
ig_d("oecd", "MEI_FIN", "IRLT-FRA-USA-DEU-JPN-2010")
```


## U.S. 10-, 20-, 30- years

```{r}
ig_d("fred", "r", "DGS10-DGS20-DGS30-2010")
```

## France - 30 ans, 10 ans, 5 ans

```{r}
ig_d("bdf", "FM", "bons-du-tresor-30ans-10ans")
```

## France, Germany, Italy, Spain, Greece

### 2005-

```{r}
ig_d("eurostat", "ei_mfir_m", "MF-LTGBY-RT-FR-DE-IT-ES-EL-2005")
```



### 2018-

```{r}
ig_d("eurostat", "ei_mfir_m", "MF-LTGBY-RT-FR-DE-IT-ES-EL-2018")
```



## France, Germany, Italy, Spain

### 2005-

```{r}
ig_d("eurostat", "ei_mfir_m", "MF-LTGBY-RT-FR-DE-IT-ES-2005")
```



### 2014-

#### Interest rates

```{r}
ig_d("eurostat", "ei_mfir_m", "MF-LTGBY-RT-FR-DE-IT-ES-2014")
```


#### Interest rates

```{r}
ig_d("eurostat", "ei_mfir_m", "MF-LTGBY-RT-FR-DE-IT-ES-spreads-2014")
```

## Europe, Germany, Portugal, Greece

### 2005-

```{r}
ig_d("eurostat", "ei_mfir_m", "MF-LTGBY-RT-EA-DE-PT-EL-2005")
```

### 2014-

```{r}
ig_d("eurostat", "ei_mfir_m", "MF-LTGBY-RT-EA-DE-PT-EL-2014")
```



# Policy interest rates

```{r, echo = F}
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -f "r.R"; /usr/local/bin/R -e 'quarto::quarto_render("r.qmd")'
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R irt_st_m; /usr/local/bin/R -e 'quarto::quarto_render("irt_st_m.qmd")'
# sh ~/iCloud/website/website_short.sh
# cd ~/iCloud/website/data/bis; /usr/local/bin/Rscript --vanilla _download_one.R CBPOL_D; /usr/local/bin/R -e 'quarto::quarto_render("CBPOL_D.qmd")'
# cd ~/iCloud/website/data/bis; /usr/local/bin/Rscript --vanilla _download_one.R CBPOL_M; /usr/local/bin/R -e 'quarto::quarto_render("CBPOL_M.qmd")'
# cd ~/iCloud/website/data/ecb; /usr/local/bin/Rscript --vanilla _download_one_csv.R FM; /usr/local/bin/R -e 'quarto::quarto_render("FM.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## ECB Main short rates rates

```{r}
ig_d("fred", "r", "ECBDFR-ECBMRRFR-ECBMLFR")
```



## Fed, ECB main short rates

### 1999-

```{r}
ig_d("bis", "CBPOL_D", "US-XM-1999")
```



## Taux BCE

```{r}
ig_d("bdf", "FM", "taux-credits-habitats")
```


## Short-term rates

```{r}
ig_d("eurostat", "irt_st_m", "IRT-M12-UK-SE-DK-EA-2000")
```

## Emerging Markets

### Brazil

```{r}
ig_d("bis", "CBPOL_M", "BR-2010")
```



# Real Interest rates

```{r, echo = F}
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -f "r.R"; /usr/local/bin/R -e 'quarto::quarto_render("r.qmd")'
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -e 'quarto::quarto_render("r.qmd")'
# sh ~/iCloud/website/website_short.sh
# cd ~/iCloud/website/data/ecb; /usr/local/bin/Rscript --vanilla _download_one_csv.R FM; /usr/local/bin/R -e 'quarto::quarto_render("FM.qmd")'
```

## ECB

```{r}
ig_d("ecb", "FM", "real-rates-USA-JPN-EUR-2010")
```

## Lending spreads

```{r}
ig_d("ecb", "FM", "A2AA225-ERIBR-WT")
```



## U.S. TIPS

### All

```{r}
ig_d("fred", "r", "DFII10-DFII20-DFII30")
```

### 2017-

```{r}
ig_d("fred", "r", "DFII10-DFII20-DFII30-2017")
```

# Corporations

```{r, echo = F}
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -f "r.R"; /usr/local/bin/R -e 'quarto::quarto_render("r.qmd")'
# cd ~/iCloud/website/data/ecb; /usr/local/bin/Rscript --vanilla _download_one_csv.R FM; /usr/local/bin/R -e 'quarto::quarto_render("FM.qmd")'
```

## AAA, BAA - United States

```{r}
ig_d("fred", "r", "AAA-BAA-2010")
```

## Loans in France, Germany, Italy

```{r}
ig_d("ecb", "MIR", "A20-2240-FR-DE-IT")
```



# Housing

```{r, echo = F}
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -f "r.R"; /usr/local/bin/R -e 'quarto::quarto_render("r.qmd")'
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -f "housing.R"; /usr/local/bin/R -e 'quarto::quarto_render("housing.qmd")'
# sh ~/iCloud/website/website_short.sh
# cd ~/iCloud/website/data/ecb; /usr/local/bin/Rscript --vanilla _download_one_csv.R MIR; /usr/local/bin/R -e 'quarto::quarto_render("MIR.qmd")'
# cd ~/iCloud/website/data/ecb/
```


## 2004-2007 Monetary Policy tightening

### Mortgage Payments

```{r}
ig_d("fred", "r", "MDSP-02-12")
```

### Fed Rates

```{r}
ig_d("fred", "r", "FEDFUNDS-02-12")
```

### Both

```{r}
i_g("bib/fred/FEDFUNDS-MDSP.png")
```






## U.S.: mortgage, Fed Funds

```{r}
ig_d("fred", "r", "MORTGAGE15US-MORTGAGE30US-FEDFUNDS-2010")
```



## Lending for house purchases, old loans

```{r}
ig_d("ecb", "MIR", "A22")
```


## Lending for house purchases

### 2010-

```{r}
ig_d("ecb", "MIR", "A2C-2010")
```

## Loans to households

```{r}
ig_d("ecb", "MIR", "A2C-2015-0-N")
```




# Miscellaneous interest rates

```{r, echo = F}
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -f "r.R"; /usr/local/bin/R -e 'quarto::quarto_render("r.qmd")'
# cd ~/iCloud/website/data/ecb; /usr/local/bin/Rscript --vanilla _download_one_csv.R MIR; /usr/local/bin/R -e 'quarto::quarto_render("MIR.qmd")'
```

## Germany

```{r}
ig_d("ecb", "MIR", "DE-A2A-2015")
```

## France

```{r}
ig_d("ecb", "MIR", "FR-A2A")
```


# Real rates (World Bank)

```{r, echo = F}
# cd ~/iCloud/website/data/wdi; /usr/local/bin/Rscript --vanilla _dl_one2.R FR.INR.RINR; /usr/local/bin/R -e 'quarto::quarto_render("FR.INR.RINR.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## UK, US, Japan

```{r}
ig_d("wdi", "FR.INR.RINR", "GB-JP-US")
```





# Info

```{r, echo = F}
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("interest-rates.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("immobilier.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("housing.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## Useful links

- CME FedWatch Tool. [html](https://www.cmegroup.com/markets/interest-rates/cme-fedwatch-tool.html)





