---
title: Data on money
subtitle: Data
author:
  - name: François Geerolf
    url: https://fgeerolf.com
format:
  html:
    code-fold: false
    toc: true
    theme: flatly
    embed-resources: false
editor: source
---


```{r, echo = FALSE, message = FALSE}
source(here::here("_rinit.R"))
invisible(Sys.setlocale("LC_TIME", "en_US.UTF-8"))
invisible(Sys.setenv(TZ = "America/Los_Angeles"))
```


# ECB


## M1

```{r}
ig_d("ecb", "BSI", "M1-E")
```


## M2-M1

```{r}
ig_d("ecb", "BSI", "M2-M1-E")
```

## M3-M2

```{r}
ig_d("ecb", "BSI", "M3-M2-E")
```



# Info





## Related papers

### English

- "Are inflation dynamics different in the euro area and the United States?" C. Blot & F. Geerolf, Monetary Dialogue Paper, November 2023, requested by the ECON committee, European Parliament. [[pdf](https://www.europarl.europa.eu/RegData/etudes/IDAN/2023/755706/IPOL_IDA(2023)755706_EN.pdf)] [[html](https://www.europarl.europa.eu/thinktank/fr/document/IPOL_IDA(2023)755706)]

- "Excess liquidity in the euro area? Assessment and possible ways forward." C. Blot, J. Creel & F. Geerolf, Monetary Dialogue Paper, September 2023, requested by the ECON committee, European Parliament. [[pdf](https://www.europarl.europa.eu/RegData/etudes/ATAG/2023/747868/IPOL_ATA(2023)747868_EN.pdf)] [[html](https://www.europarl.europa.eu/thinktank/en/document/IPOL_ATA(2023)747868)]

- "Is monetary tightening a threat to financial stability?" C. Blot, J. Creel & F. Geerolf, Monetary Dialogue Paper, June 2023, requested by the ECON committee, European Parliament. [[pdf](https://www.europarl.europa.eu/RegData/etudes/IDAN/2023/747843/IPOL_IDA(2023)747843_EN.pdf)] [[html](https://www.europarl.europa.eu/thinktank/en/document/IPOL_IDA(2023)747843)]

- "The direct and indirect impacts of the war on inflation." C. Blot, J. Creel & F. Geerolf, Monetary Dialogue Paper, March 2023, requested by the ECON committee, European Parliament. [[pdf](https://www.europarl.europa.eu/RegData/etudes/IDAN/2023/741487/IPOL_IDA(2023)741487_EN.pdf)] [[html](https://www.europarl.europa.eu/thinktank/en/document/IPOL_IDA(2023)741487)]

- "Heterogeneity of inflation in the euro area: more complicated than it seems." C. Blot, J. Creel, F. Geerolf & S. Levasseur, Monetary Dialogue Paper, November 2022, requested by the ECON committee, European Parliament. [[pdf](https://www.europarl.europa.eu/RegData/etudes/IDAN/2022/733999/IPOL_IDA(2022)733999_EN.pdf)] [[html](https://www.europarl.europa.eu/thinktank/en/document/IPOL_IDA(2022)733999)]

- 

### Français






