---
title: Data on monetary policy
metadata-files: 
  - _common.yml
---


```{r, echo = FALSE, message = FALSE}
source(here::here("_rinit.R"))
invisible(Sys.setlocale("LC_TIME", "en_US.UTF-8"))
invisible(Sys.setenv(TZ = "America/Los_Angeles"))
`monetary-policy` <- tribble(
  ~source, ~dataset,
  "bdf",  "FM",
  "bdf",  "MIR",
  "bdf",  "MIR1",
  "bis",  "CBPOL",
  "ecb", "BSI",
  "ecb", "BSI_PUB",
  "ecb",  "FM",
  "ecb", "ILM",
  "ecb", "ILM_PUB",
  "ecb", "liq_daily",
  "ecb",  "MIR",
  "ecb", "RAI",
  "ecb",  "SUP",
  "ecb",  "YC",
  "ecb",  "YC_PUB",
  "eurostat", "ei_mfir_m",
  "eurostat", "irt_st_m",
  "fred",  "r",
  "oecd",  "MEI",
  "oecd",  "MEI_FIN") %>%
  arrange(source, dataset)
```


# Liquidity

```{r, echo = F}
# Download from Chrome: https://sdw-wsrest.ecb.europa.eu/service/data/BSI?format=csvdata
# Download from Chrome: https://sdw-wsrest.ecb.europa.eu/service/data/QSA?format=csvdata
# Download from Chrome: https://sdw-wsrest.ecb.europa.eu/service/data/YC?format=csvdata
# cd ~/iCloud/website/data/ecb; /usr/local/bin/Rscript --vanilla _download_one_csv_manual.R YC; /usr/local/bin/R -e 'quarto::quarto_render("YC.qmd")'
# cd ~/iCloud/website/data/ecb; /usr/local/bin/Rscript --vanilla _download_one_csv_manual.R QSA; /usr/local/bin/R -e 'quarto::quarto_render("QSA.qmd")'
# cd ~/iCloud/website/data/ecb; /usr/local/bin/Rscript --vanilla _download_one_csv_manual.R BSI; /usr/local/bin/R -e 'quarto::quarto_render("BSI.qmd")'
# sh ~/iCloud/website/website_short.sh
# cd ~/iCloud/website/data/ecb; /usr/local/bin/Rscript --vanilla _download_one_csv.R BSI_PUB; /usr/local/bin/R -e 'quarto::quarto_render("BSI_PUB.qmd")'
# /usr/local/bin/R -e 'quarto::quarto_render("QSA.qmd")'
# sh ~/iCloud/website/website_short.sh
```


## M1, M2, M3

### BSI

```{r}
ig_d("ecb", "BSI", "M1-M2-M3-A")
```

### Short

```{r}
ig_d("ecb", "BSI_PUB", "M1-M2-M3-A")
```


## Loans to households

### All

```{r}
ig_d("ecb", "BSI", "adjusted-loans-households-FR-DE-IT-U2")
```


### 2016-

```{r}
ig_d("ecb", "BSI", "adjusted-loans-households-FR-DE-IT-U2-2016")
```


## Loans to NFCs

### All

```{r}
ig_d("ecb", "BSI", "adjusted-loans-NFC-FR-DE-IT-U2")
```



### 2016-

```{r}
ig_d("ecb", "BSI", "adjusted-loans-NFC-FR-DE-IT-U2-2016")
```

# Long-term rates

```{r, echo = F}
# cd ~/iCloud/website/data/oecd; /usr/local/bin/R -f MEI_16.R; /usr/local/bin/R -e 'quarto::quarto_render("MEI.qmd")'
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -f "r.R"; /usr/local/bin/R -e 'quarto::quarto_render("r.qmd")'
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R ei_mfir_m; /usr/local/bin/R -e 'quarto::quarto_render("ei_mfir_m.qmd")'
# cd ~/iCloud/website/data/oecd; /usr/local/bin/Rscript --vanilla _download_data.R MEI_FIN; /usr/local/bin/R -e 'quarto::quarto_render("MEI_FIN.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## U.S., France, Japan, Germany

```{r}
ig_d("oecd", "MEI_FIN", "IRLT-FRA-USA-DEU-JPN-2010")
```


## U.S. 10-, 20-, 30- years

```{r}
ig_d("fred", "r", "DGS10-DGS20-DGS30-2010")
```

## France - 30 ans, 10 ans, 5 ans

```{r}
ig_d("bdf", "FM", "bons-du-tresor-30ans-10ans")
```

## France, Germany, Italy, Spain, Greece

### 2005-

```{r}
ig_d("eurostat", "ei_mfir_m", "MF-LTGBY-RT-FR-DE-IT-ES-EL-2005")
```



### 2018-

```{r}
ig_d("eurostat", "ei_mfir_m", "MF-LTGBY-RT-FR-DE-IT-ES-EL-2018")
```

## France, Germany, Italy, Spain

### 2005-

```{r}
ig_d("eurostat", "ei_mfir_m", "MF-LTGBY-RT-FR-DE-IT-ES-2005")
```



### 2014-

#### Interest rates

```{r}
ig_d("eurostat", "ei_mfir_m", "MF-LTGBY-RT-FR-DE-IT-ES-2014")
```


#### Interest rates

```{r}
ig_d("eurostat", "ei_mfir_m", "MF-LTGBY-RT-FR-DE-IT-ES-spreads-2014")
```

## Europe, Germany, Portugal, Greece

### 2005-

```{r}
ig_d("eurostat", "ei_mfir_m", "MF-LTGBY-RT-EA-DE-PT-EL-2005")
```

### 2014-

```{r}
ig_d("eurostat", "ei_mfir_m", "MF-LTGBY-RT-EA-DE-PT-EL-2014")
```




# Policy interest rates

```{r, echo = F}
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -f "r.R"; /usr/local/bin/R -e 'quarto::quarto_render("r.qmd")'
# cd ~/iCloud/website/data/bis; /usr/local/bin/Rscript --vanilla _download_one.R CBPOL; /usr/local/bin/R -e 'quarto::quarto_render("CBPOL.qmd")'
# cd ~/iCloud/website/data/bis; /usr/local/bin/Rscript --vanilla _download_one.R CBPOL_M; /usr/local/bin/R -e 'quarto::quarto_render("CBPOL_M.qmd")'
# cd ~/iCloud/website/data/ecb; /usr/local/bin/Rscript --vanilla _download_one_csv.R FM; /usr/local/bin/R -e 'quarto::quarto_render("FM.qmd")'
```

## ECB Main short rates rates

### All

```{r}
ig_d("fred", "r", "ECBDFR-ECBMRRFR-ECBMLFR")
```

### 2022-

```{r}
ig_d("ecb", "FM", "DFR-MLFR-MRRRT-2022")
```


### Dates of monetary policy meetings

```{r}
ig_d("ecb", "FM", "DFR-MLFR-MRRRT-2022-dateschange")
```




## Fed, ECB main short rates

### 2022-

```{r}
ig_d("bis", "CBPOL_D", "US-XM-2022-dates2-deposit")
```



### 1999-

```{r}
ig_d("bis", "CBPOL", "US-XM-1999")
```


### Monthly

```{r}
ig_d("bis", "CBPOL_M", "US-JP-XM-1985")
```



# Real Interest rates

```{r, echo = F}
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -f "r.R"; /usr/local/bin/R -e 'quarto::quarto_render("r.qmd")'
# cd ~/iCloud/website/data/ecb; /usr/local/bin/Rscript --vanilla _download_one_csv.R FM; /usr/local/bin/R -e 'quarto::quarto_render("FM.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## ECB

### All

```{r}
ig_d("ecb", "FM", "real-rates-USA-JPN-EUR")
```



### 1999-

```{r}
ig_d("ecb", "FM", "real-rates-USA-EUR-1999")
```

### 2010-

```{r}
ig_d("ecb", "FM", "real-rates-USA-JPN-EUR-2010")
```

## Lending spreads

```{r}
ig_d("ecb", "FM", "A2AA225-ERIBR-WT")
```



## U.S. TIPS

```{r}
ig_d("fred", "r", "DFII10-DFII20-DFII30-2017")
```

# Corporations

```{r, echo = F}
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -f "r.R"; /usr/local/bin/R -e 'quarto::quarto_render("r.qmd")'
# sh ~/iCloud/website/website_short.sh
# cd ~/iCloud/website/data/ecb; /usr/local/bin/Rscript --vanilla _download_one_csv.R FM; /usr/local/bin/R -e 'quarto::quarto_render("FM.qmd")'
# cd ~/iCloud/website/data/ecb/
```

## AAA, BAA - United States

```{r}
ig_d("fred", "r", "AAA-BAA-2010")
```

## Loans in France, Germany, Italy

```{r}
ig_d("ecb", "MIR", "A20-2240-FR-DE-IT")
```


# Housing

```{r, echo = F}
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -f "r.R"; /usr/local/bin/R -e 'quarto::quarto_render("r.qmd")'
# sh ~/iCloud/website/website_short.sh
# cd ~/iCloud/website/data/ecb; /usr/local/bin/Rscript --vanilla _download_one_csv.R MIR; /usr/local/bin/R -e 'quarto::quarto_render("MIR.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## U.S.: mortgage, Fed Funds

```{r}
ig_d("fred", "r", "MORTGAGE15US-MORTGAGE30US-FEDFUNDS-2010")
```



## Lending for house purchases, old loans

### France, Belgium, Germany, Netherlands

```{r}
ig_d("ecb", "MIR", "A22-2018-FR-BE-DE-NL")
```

### France, Germany, Italy, Spain, Netherlands

```{r}
ig_d("ecb", "MIR", "A22")
```

### Estonia, Lithuania, Latvia, Portugal, Finland, Spain

```{r}
ig_d("ecb", "MIR", "A22-2018-EE-LT-LV-PT-FI-ES")
```



## Lending for house purchases

```{r}
ig_d("ecb", "MIR", "A2C-2010")
```


# Miscellaneous interest rates

```{r, echo = F}
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -f "r.R"; /usr/local/bin/R -e 'quarto::quarto_render("r.qmd")'
# sh ~/iCloud/website/website_short.sh
# cd ~/iCloud/website/data/ecb; /usr/local/bin/Rscript --vanilla _download_one_csv.R MIR; /usr/local/bin/R -e 'quarto::quarto_render("MIR.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## Germany

```{r}
ig_d("ecb", "MIR", "DE-A2A-2015")
```

## France

```{r}
ig_d("ecb", "MIR", "FR-A2A")
```


# Target Balances

```{r, echo = F}
# cd ~/iCloud/website/data/ecb; /usr/local/bin/Rscript --vanilla _download_one_csv.R TGB; /usr/local/bin/R -e 'quarto::quarto_render("TGB.qmd")'
# sh ~/iCloud/website/website_short.sh
```


## France, Germany, Italy, Greece

```{r}
ig_d("ecb", "TGB", "TGB-A")
```


# Variable VS fixed rates

```{r, echo = F}
# cd ~/iCloud/website/data/ecb; /usr/local/bin/Rscript --vanilla _download_one_csv.R RAI; /usr/local/bin/R -e 'quarto::quarto_render("RAI.qmd")'
# sh ~/iCloud/website/website_short.sh
```



## France, Germany, Netherlands, Belgium, Europe

```{r}
ig_d("ecb", "RAI", "SVLHPHH-NL-DE-BE-FR-U2")
```



## France, Spain, Portugal, Estonia, Lithuania

```{r}
ig_d("ecb", "RAI", "SVLHPHH-FR-ES-PT-EE-LT-U2")
```



## France, Spain, Portugal

```{r}
ig_d("ecb", "RAI", "SVLHPHH-FR-ES-PT")
```


## Poland, Australia, Sweden

```{r}
ig_d("ecb", "RAI", "SVLHPHH-PL-AU-SE")
```



# Yield Curve

```{r, echo = F}
# MANUAL download from internet then run _download_one_csv_manual.R (download with Chrome, end with fread)
# https://sdw-wsrest.ecb.europa.eu/service/data/YC?format=csvdata
# cd ~/iCloud/website/data/ecb; /usr/local/bin/Rscript --vanilla _download_one_csv_manual.R YC; /usr/local/bin/R -e 'quarto::quarto_render("YC.qmd")'
# cd ~/iCloud/website/data/ecb; /usr/local/bin/Rscript --vanilla _download_one_csv.R YC_PUB; /usr/local/bin/R -e 'quarto::quarto_render("YC_PUB.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## Yield Curve

```{r}
ig_d("ecb", "YC", "G-N-C-log2")
```

## 2 year rate

```{r}
ig_d("ecb", "YC", "PY-2Y")
```



## 10 year rate

```{r}
ig_d("ecb", "YC", "PY-10Y")
```

## 1 year, 10 years

```{r}
ig_d("ecb", "YC_PUB", "SR-1Y-10Y")
```

## 2 years, 5 years, 7 years

```{r}
ig_d("ecb", "YC_PUB", "SR-2Y-5Y-7Y")
```




# Liquidity

```{r, echo = F}
# cd ~/iCloud/website/data/ecb; /usr/local/bin/Rscript --vanilla _download_one_csv.R ILM; /usr/local/bin/R -e 'quarto::quarto_render("ILM.qmd")'
# cd ~/iCloud/website/data/ecb; /usr/local/bin/Rscript --vanilla _download_one_csv.R ILM_PUB; /usr/local/bin/R -e 'quarto::quarto_render("ILM_PUB.qmd")'
# cd ~/iCloud/website/data/ecb; /usr/local/bin/R -f "liq_daily.R"; /usr/local/bin/R -e 'quarto::quarto_render("liq_daily.qmd")'
# sh ~/iCloud/website/website_short.sh
```


## Banknotes

```{r}
ig_d("ecb", "BKN", "banknotes")
```


## Main Refinancing Operation

```{r}
ig_d("ecb", "ILM", "MRO-FR-DE-IT")
```



## Liquidity-providing: LTRO, MRO, MLF, NFA

```{r}
ig_d("ecb", "ILM", "liquidity-providing")
```

## Liquidity-absorbing

```{r}
ig_d("ecb", "ILM", "liquidity-absorbing")
```


## Programs

##

```{r}
ig_d("ecb", "liq_daily", "CBPP1-CBPP2-CBPP3-SMP-ABSPP-PSPP-CSPP-PEPP-2022")
```

## Excess liquidity

```{r}
ig_d("ecb", "liq_daily", "synthesis")
```


## Deposit facility

```{r}
ig_d("ecb", "liq_daily", "excess-liq-deposit-facility-current-accounts-2022")
```

# Bank Lending Survey

```{r, echo = F}
# cd ~/iCloud/website/data/ecb; /usr/local/bin/Rscript --vanilla _download_one_csv.R BLS; /usr/local/bin/R -e 'quarto::quarto_render("BLS.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## Consumer credit + Lending for house purchases

```{r}
ig_d("ecb", "BLS", "BLS.Q.U2.ALL.Z.H.H-C.B3.ZZ.D.WFNET")
```


# Supervisory Statistics

```{r, echo = F}
# cd ~/iCloud/website/data/ecb; /usr/local/bin/Rscript --vanilla _download_one_csv.R SUP; /usr/local/bin/R -e 'quarto::quarto_render("SUP.qmd")'
# sh ~/iCloud/website/website_short.sh
```


## France, Italy, Germany, Spain, Netherlands, 

```{r}
ig_d("ecb", "SUP", "net-interest-margin-FR-IT-DE-ES-NL-SI")
```

## France, Italy, Germany, Spain, Netherlands, Belgium, Austria, Portugal

```{r}
ig_d("ecb", "SUP", "net-interest-margin-FR-IT-DE-ES-NL-BE-AT-PT")
```



# Linked Themes

```{r, echo = F}
tribble(~ theme,
        "monetary-policy",
        "interest-rates") |>
  theme_file_updates()
```


# Datasets

```{r, echo = F}
`monetary-policy` |>
  source_dataset_file_updates()
```



# Bibliography

{{< include ../publications/monetary-policy.qmd >}}
