---
title: Overview of Public Debt Statistics
metadata-files: 
  - _common.yml
---

```{r, echo = FALSE, message = FALSE}
source(here::here("_rinit.R"))
invisible(Sys.setlocale("LC_TIME", "en_US.UTF-8"))
invisible(Sys.setenv(TZ = "America/Los_Angeles"))

`public-debt` <- tribble(
  ~source, ~dataset,
  "eurostat",  "ei_mfir_m",
  "eurostat",  "gov_10q_ggdebt",
  "fred",  "r",
  "fred",  "saving",
  "gfd",  "debt",
  "imf",  "FM",
  "imf",  "HPDD",
  "imf",  "GGXWDN_G01_GDP_PT",
  "imf", "GGXONLB_G01_GDP_PT",
  "imf", "GGXCNL_G01_GDP_PT",
  "oecd", "QASA_TABLE7PSD",
  "wdi",  "GC.XPN.INTP.ZS",
  "wdi",  "GC.XPN.INTP.CN",
  "wdi",  "GC.DOD.TOTL.GD.ZS",
  "wdi",  "GC.XPN.INTP.RV.ZS") %>%
  arrange(source, dataset)
```


```{r, echo = F}
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("dette-publique.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("public-debt.qmd")'
# sh ~/iCloud/website/website_short.sh
```


# Sovereign rates

```{r, echo = F}
temp <- "https://tradingeconomics.com/country-list/rating" |>
  rvest::read_html() |>
  rvest::html_table(header = T, fill = T)

ratings <- temp[[1]] |>
  rename(country = 1)

temp <- "https://www.investing.com/rates-bonds/world-government-bonds" |>
  rvest::read_html() |>
  rvest::html_table(header = T, fill = T)

# length(temp) - 4 car les.4 dernières tibble ne sont pas des données de taux souverains
# on enlève les warnings pour la transformation de Chg. en numeric

taux_souverains <- tibble(num = 1:(length(temp)-4)) %>%
  mutate(data = map(num, ~ temp[[.]] %>%
                      select(2:7) %>%
                      mutate(`Chg.` = suppressWarnings(as.numeric(`Chg.`))))) %>%
  unnest(cols = c(data)) %>%
  select(-num) %>%
  mutate(duration = str_extract(Name, "\\d+[YM]$"),
         country = str_trim(str_extract(Name, "^[\\p{L} .'’]+")),
         country = case_when(country == "U.S." ~ "United States",
                             country == "U.K." ~ "United Kingdom",
                             T ~ country)) %>%
  mutate(country = ifelse(country == "Cote d'Ivoire", "Ivory Coast", country)) %>%
  select(-Name) %>%
  select(country, duration, everything())
```


## 5Y, 10Y, 30Y

```{r, echo = F}
country_codes <- codelist |>
  select(country = country.name.en, country_code_2 = genc2c)

taux_souverains %>%
  filter(duration %in% c("5Y", "10Y", "30Y")) %>%
  select(country, duration, Yield) %>%
  spread(duration, Yield) |>
  left_join(country_codes, by = "country") |>
  select(country_code_2, country, `10Y`, `30Y`, everything()) |>
  arrange(`10Y`) |>
  filter(!is.na(country)) |>
  gt()|>
    tab_options(
      quarto.disable_processing = TRUE
    ) |> 
  cols_align(
    align = "center",
    columns = -c(country))|>
  cols_label(
    country = "",
    country_code_2 = ""
    )|>
  fmt_number(
    dec_mark = ",",
    sep_mark = ".",
    decimals = 2
  ) |>
  fmt_flag(columns = country_code_2) |>
  sub_missing(
    missing_text = ""
  )|>
  opt_interactive(
    use_search = F,
    use_pagination = T,
    use_pagination_info = F,
    use_compact_mode = T,
    page_size_default = 20,
    page_size_values = c(20, 30, 50, 100),
    use_resizers = T,
    use_highlight = T
  ) |>
  gt::tab_source_note(
    source_note = gt::md(paste0("Date: ", format(Sys.time(), format = "%B %d, %Y %I:%M %p"), ". Source: <https://www.investing.com/rates-bonds/world-government-bonds>"))
  ) |>
  gt::tab_options(table.width = "100%")
```



## 10Y, 30Y, ratings

```{r, echo = F}
ratings_taux <- taux_souverains %>%
  filter(duration %in% c("10Y", "30Y")) %>%
  select(country, duration, Yield) %>%
  spread(duration, Yield) %>%
  left_join(ratings, by = "country")

country_codes <- codelist |>
  select(country = country.name.en, country_code_2 = genc2c)

ratings_taux |>
  left_join(country_codes, by = "country") |>
  select(-DBRS) |>
  select(country_code_2, country, everything()) |>
  arrange(-TE, `10Y`) |>
  select(-TE) |>
  filter(!is.na(country)) |>
  gt()|>
    tab_options(
      quarto.disable_processing = TRUE
    ) |> 
  cols_align(
    align = "center",
    columns = -c(country))|>
  cols_label(
    country = "",
    country_code_2 = ""
    )|>
  fmt_number(
    dec_mark = ",",
    sep_mark = ".",
    decimals = 2
  ) |>
  fmt_flag(columns = country_code_2) |>
  sub_missing(
    missing_text = ""
  )|>
  opt_interactive(
    use_search = F,
    use_pagination = T,
    use_pagination_info = F,
    use_compact_mode = T,
    page_size_default = 20,
    page_size_values = c(20, 30, 50, 100),
    use_resizers = T,
    use_highlight = T
  ) |>
  gt::tab_source_note(
    source_note = gt::md(paste0("Date: ", format(Sys.time(), format = "%B %d, %Y %I:%M %p"), ". Source: <https://www.investing.com/rates-bonds/world-government-bonds>"))
  ) |>
  gt::tab_options(table.width = "100%")
```

# Public debt data

```{r, echo = F}
# cd ~/iCloud/website/data/imf; /usr/local/bin/Rscript --vanilla _download_one.R FM G_XWDG_G01_GDP_PT ; /usr/local/bin/R -e 'quarto::quarto_render("G_XWDG_G01_GDP_PT.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## Fiscal Monitor

```{r}
ig_d("imf", "G_XWDG_G01_GDP_PT", "FRA-DEU-USA-ITA-JPN")
```



# U.S.

```{r, echo = F}
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -f "saving.R"; /usr/local/bin/R -e 'quarto::quarto_render("saving.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## Public deficit

### Last

```{r}
ig_d("fred", "saving", "US-deficit-GDP")
```


### 1947-

```{r}
ig_d("fred", "saving", "US-deficit-GDP-1947")
```

### 1999-

```{r}
ig_d("fred", "saving", "US-deficit-GDP-1999")
```



# Europe

```{r, echo = F}
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R gov_10q_ggdebt; /usr/local/bin/R -e 'quarto::quarto_render("gov_10q_ggdebt.qmd")'
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R ei_mfir_m; /usr/local/bin/R -e 'quarto::quarto_render("ei_mfir_m.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## Debt to GDP ratios (years)

```{r, echo = F}
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R gov_10q_ggdebt; /usr/local/bin/R -e 'quarto::quarto_render("gov_10q_ggdebt.qmd")'
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/R -e 'quarto::quarto_render("gov_10q_ggdebt.qmd")'
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
# sh ~/iCloud/website/website_short.sh
```

### Last

```{r}
ig_d("eurostat", "gov_10q_ggdebt", "GD-US-UK-FR-JP-IT")
```


### 2015-

```{r, out.width="100%"}
ig_d("eurostat", "gov_10q_ggdebt", "GD-US-UK-FR-JP-IT-2015")
```


### 2015- (%)

```{r, out.width="100%"}
ig_d("eurostat", "gov_10q_ggdebt", "GD-US-UK-FR-JP-IT-2015-percent")
```



### Other countries

```{r, out.width="100%"}
ig_d("eurostat", "gov_10q_ggdebt", "NL-LU-DK-SE-FR")
```

## Deficits

```{r, echo = F}
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R gov_10dd_edpt1; /usr/local/bin/R -e 'quarto::quarto_render("gov_10dd_edpt1.qmd")'
# sh ~/iCloud/website/website_short.sh
```


### Portugal, Greece, Germany, Euro area

#### All

```{r}
ig_d("eurostat", "gov_10dd_edpt1", "FR-DE-IT-ES-NL-B9")
```



## Interest rates

```{r, echo = F}
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R ei_mfir_m; /usr/local/bin/R -e 'quarto::quarto_render("ei_mfir_m.qmd")'
# sh ~/iCloud/website/website_short.sh
```

### Germany, Italy, France, Spain

```{r}
ig_d("eurostat", "ei_mfir_m", "MF-LTGBY-RT-FR-DE-IT-ES-2005")
```


### Portugal, Greece, Germany, Euro area

```{r}
ig_d("eurostat", "ei_mfir_m", "MF-LTGBY-RT-EA-DE-PT-EL-2014")
```

# IMF

```{r, echo = F}
# cd ~/iCloud/website/data/imf; /usr/local/bin/Rscript --vanilla _download_one.R FM GGXCNL_G01_GDP_PT ; /usr/local/bin/R -e 'quarto::quarto_render("GGXCNL_G01_GDP_PT.qmd")'
# cd ~/iCloud/website/data/imf; /usr/local/bin/Rscript --vanilla _download_one.R FM GGXONLB_G01_GDP_PT ; /usr/local/bin/R -e 'quarto::quarto_render("GGXONLB_G01_GDP_PT.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## Primary and Total Deficits



## Total deficit

### United States, France, Europe

```{r}
ig_d("imf", "GGXCNL_G01_GDP_PT", "U2-US-FR-2010")
```


### United States, France, Europe

```{r}
ig_d("imf", "GGXCNL_G01_GDP_PT", "U2-US-FR-2010")
```

### Euopean countries, U.S.

#### All

```{r}
ig_d("imf", "GGXCNL_G01_GDP_PT", "IT-FR-DE-ES-US")
```



#### 2010-

```{r}
ig_d("imf", "GGXCNL_G01_GDP_PT", "IT-FR-DE-ES-US-2010")
```



### France, Germany, U.S., E.U.

#### All

```{r}
ig_d("imf", "GGXCNL_G01_GDP_PT", "FR-DE-US-U2")
```



#### 2005-

```{r}
ig_d("imf", "GGXCNL_G01_GDP_PT", "FR-DE-US-U2-2008")
```



## Primary deficit

### Euopean countries, U.S.

```{r}
ig_d("imf", "GGXCNL_G01_GDP_PT", "IT-FR-DE-ES-US")
```


## Public Debt

### Long Period

```{r}
ig_d("imf", "HPDD", "US-UK-FR-JP-IT")
```



### Long Period

```{r}
ig_d("imf", "HPDD", "US-UK-FR-JP-IT")
```

# OECD

```{r, echo = F}
# cd ~/iCloud/website/data/oecd; /usr/local/bin/Rscript --vanilla _download_data.R QASA_TABLE7PSD; /usr/local/bin/R -e 'quarto::quarto_render("QASA_TABLE7PSD.qmd")'
# sh ~/iCloud/website/website_short.sh
```


## France, United States

```{r}
ig_d("oecd", "QASA_TABLE7PSD", "SAFGD-CXCAR-FRA-USA-log")
```


## France, UK, Italy, Canada

```{r}
ig_d("oecd", "QASA_TABLE7PSD", "SAFGD-CXCAR-FRA-GBR-ITA-CAN")
```

# France

```{r, echo = F}
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
# cd ~/iCloud/website/data/insee; /usr/local/bin/R -e 'quarto::quarto_render("T_3201.qmd")'
# cd ~/iCloud/website/data/insee; /usr/local/bin/R -e 'quarto::quarto_render("t_compteapu_val.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## Trajectory (Source: Oxford Economics)

```{r}
ig_b("debt", "france-trajectory-march2024")
```


## Charge d'intérêt

```{r}
ig_d("insee", "T_3201", "line7")
```



## Déficit primaire VS total

### Tous

```{r}
ig_d("insee", "t_compteapu_val", "PIB-D41-B9NF")
```



### 2005-

```{r}
ig_d("insee", "t_compteapu_val", "PIB-D41-B9NF-2005")
```



## Charge d'intérêt

```{r}
ig_d("insee", "t_compteapu_val", "PIB-D41")
```

# Rating agencies

## Risk weights

```{r}
ig_b("bis", "CRE20", "sovereign-rating")
```

# Détention par les non-résidents de la dette / CAC40

```{r, echo = F}
# cd ~/iCloud/website/data/bdf; /usr/local/bin/Rscript --vanilla _download_one.R DET; /usr/local/bin/R -e 'quarto::quarto_render("DET.qmd")'
# sh ~/iCloud/website/website_short.sh
```


## Detention

```{r}
ig_d("bdf", "DET", "detention-non-residents")
```



# Datasets

```{r, echo = F}
`public-debt` |>
  source_dataset_file_updates()
```

# Bibliography

## English

{{< include ../public-debate/en/Geerolf2025.qmd >}}

{{< include ../publications/en/Geerolf2024b.qmd >}}

{{< include ../working-papers/en/Geerolf2018a.qmd >}}

{{< include ../publications/en/Geerolf2013.qmd >}}

## French

{{< include ../public-debate/fr/Geerolf2025.qmd >}}

{{< include ../publications/fr/Geerolf2024b.qmd >}}

{{< include ../public-debate/fr/EcalleGeerolf2025.qmd >}}

{{< include ../publications/fr/Geerolf2021c.qmd >}}

{{< include ../publications/fr/Geerolf2021c.qmd >}}


