---
title: Wage Data
metadata-files: 
  - _common.yml
---

```{r, echo = FALSE, message = FALSE}
source(here::here("_rinit.R"))
invisible(Sys.setlocale("LC_TIME", "en_US.UTF-8"))
invisible(Sys.setenv(TZ = "America/Los_Angeles"))
wages <- tribble(
  ~source, ~dataset,
  "eurostat",  "earn_mw_cur",
  "eurostat", "tps00155",
  "eurostat",  "ei_lmlc_q",
  "eurostat",  "lc_lci_lev",
  "eurostat",  "lc_lci_r2_q",
  "eurostat",  "nama_10_lp_ulc",
  "eurostat",  "namq_10_lp_ulc",
  "fred",  "wage",
  "ilo",  "EAR_XEES_SEX_ECO_NB_Q",
  "ilo",  "EAR_4MTH_SEX_ECO_CUR_NB_A",
  "oecd",  "AV_AN_WAGE",
  "oecd",  "HH_DASH",
  "oecd",  "EAR_MEI",
  "oecd",  "AWCOMP",
  "oecd",  "MIN2AVE",
  "oecd",  "RMW",
  "oecd",  "ULC_EEQ") %>%
  arrange(source, dataset)
```

# Info

```{r, echo = F}
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("wages.qmd")'
# sh ~/iCloud/website/website_short.sh
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("salaires.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("wages.qmd")'
# sh ~/iCloud/website/website_short.sh; open https://fgeerolf.com/data/macro-france.html
# sh ~/iCloud/website/website_short.sh; open https://fgeerolf.com/data/inflation-france.html
# sh ~/iCloud/website/website_short.sh
```





# OECD Data

```{r, echo = F}
# cd ~/iCloud/website/data/oecd; /usr/local/bin/Rscript --vanilla _download_data.R EAR_MEI; /usr/local/bin/R -e 'quarto::quarto_render("EAR_MEI.qmd")'
# cd ~/iCloud/website/data/oecd; /usr/local/bin/R -f PRICES_CPI_5.R; /usr/local/bin/R -e 'quarto::quarto_render("PRICES_CPI.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## US, EU, UK

### 1996-

```{r}
ig_d("oecd", "EAR_MEI", "LCEAPRIXOBSA-USA-EA19-GBR-1996-real")
```


### 2015-

```{r}
ig_d("oecd", "EAR_MEI", "LCEAPRIXOBSA-USA-EA19-GBR-FRA-2015-real")
```

## France, Germany, Italy, Belgium, Spain, Portugal, Austria

### 2015-

```{r}
ig_d("oecd", "EAR_MEI", "LCEAPRIXOBSA-FRA-DEU-ITA-BEL-ESP-PRT-AUT-2015-real")
```



### 2019Q4-

```{r}
ig_d("oecd", "EAR_MEI", "LCEAPRIXOBSA-FRA-DEU-ITA-BEL-ESP-PRT-AUT-2015-real")
```

# United States vs. Euro area



# United States

```{r, echo = F}
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -f wage.R
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -f cpi.R
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -e 'quarto::quarto_render("wage.qmd")'
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -e 'quarto::quarto_render("cpi.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## Employment cost Index

### All

```{r}
ig_d("fred", "wage", "ECI")
```


### 2019-

```{r}
ig_d("fred", "wage", "ECI-2019")
```



## U.S. Real Wages

### All

```{r}
ig_d("fred", "wage", "real-wages")
```

### 1970-

```{r}
ig_d("fred", "wage", "real-wages-1970")
```

# Europe wages

```{r, echo = F}
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R lc_lci_r2_q; /usr/local/bin/R -e 'quarto::quarto_render("lc_lci_r2_q.qmd")'
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
# sh ~/iCloud/website/website_short.sh
# cd ~/iCloud/website/data/oecd; /usr/local/bin/Rscript --vanilla _download_data.R EAR_MEI; /usr/local/bin/R -e 'quarto::quarto_render("EAR_MEI.qmd")'
# sh ~/iCloud/website/website_short.sh
```


## Negociated wages

- Definition. [pdf](https://www.ecb.europa.eu/pub/pdf/other/mb200209_focus05.en.pdf)

```{r}
ig_d("ecb", "STS", "M-I8-N-UNEH-RTT000-4-000-2017")
```



## Wages and salaries

### 2017T2-2024T2

```{r}
ig_d("eurostat", "lc_lci_r2_q", "FR-B-S-SCA-D11-2017T2")
```



### Growth

```{r}
ig_d("eurostat", "lc_lci_r2_q", "FR-DE-ES-IT-B-S-D11-2020")
```

### Growth

```{r}
ig_d("eurostat", "lc_lci_r2_q", "FR-DE-ES-IT-B-S-D11-2020")
```

## Labour costs other than wages and salaries

```{r}
ig_d("eurostat", "lc_lci_r2_q", "FR-DE-ES-IT-B-S-D12D4MD5-2020")
```


## Labour costs other than wages and salaries

```{r}
ig_d("eurostat", "lc_lci_r2_q", "FR-DE-ES-IT-B-S-D12D4MD5-2020")
```




## Labour costs for LCI

```{r}
ig_d("eurostat", "lc_lci_r2_q", "FR-DE-ES-IT-B-S-D1D4MD5-2020")
```



## Minimum wages

```{r}
ig_d("oecd", "EAR_MEI", "LCEAPRIXOBSA-USA-EA19-GBR-FRA-2015-real")
```

# Real minimum wages - OECD

```{r, echo = F}
# cd ~/iCloud/website/data/oecd; /usr/local/bin/Rscript --vanilla _download_data.R RMW; /usr/local/bin/R -e 'quarto::quarto_render("RMW.qmd")'
# cd ~/iCloud/website/data/oecd; /usr/local/bin/R -f PRICES_CPI_5.R
# cd ~/iCloud/website/data/oecd
# cd ~/iCloud/website/data/oecd; /usr/local/bin/R -e 'quarto::quarto_render("EAR_MEI.qmd")'
# sh ~/iCloud/website/website_short.sh
```


## US, France, Germany, Italy

```{r}
ig_d("oecd", "RMW", "PPP-H-FRA-USA-DEU-ITA-ESP")
```


# France Example: Differences

```{r, echo = F}
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R nama_10_lp_ulc; /usr/local/bin/R -e 'quarto::quarto_render("nama_10_lp_ulc.qmd")'
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## Compensation, Nominal unit labour cost, Real labour productivity

```{r}
ig_d("eurostat", "nama_10_lp_ulc", "RLPRPER-D1SALPER-NULCPER-FR-values")
```



## Compensation, Nominal unit labour cost, Real labour productivity

```{r}
ig_d("eurostat", "nama_10_lp_ulc", "RLPRPER-D1SALPER-NULCPER-FR-values")
```



# Wages in the Long Run

```{r, echo = F}
# cd ~/iCloud/website/data/eurostat
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R namq_10_lp_ulc
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _metadata_one.R direct
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R nama_10_lp_ulc; /usr/local/bin/R -e 'quarto::quarto_render("nasq_10_nf_tr.qmd")'
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/R -e 'quarto::quarto_render("nama_10_lp_ulc.qmd")'
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/R -e 'quarto::quarto_render("namq_10_lp_ulc.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## France

```{r}
ig_d("eurostat", "nama_10_lp_ulc", "D1-SAL-HW-FR")
```



## Poland, Hungary, Croatia

```{r}
ig_d("eurostat", "nama_10_lp_ulc", "D1-SAL-HW-HR-PL-HU-NAC-index")
```





## Poland, Hungary, Croatia

```{r}
ig_d("eurostat", "nama_10_lp_ulc", "D1-SAL-HW-HR-PL-HU-NAC-index")
```


