---
title: Exchange Rate Data
subtitle: Data
author:
  - name: François Geerolf
    url: https://fgeerolf.com
format:
  html:
    code-fold: false
    toc: true
    theme: flatly
    embed-resources: false
editor: source
---

```{r, echo = FALSE, message = FALSE, warning = FALSE}
source(here::here("_rinit.R"))
invisible(Sys.setlocale("LC_TIME", "en_US.UTF-8"))
invisible(Sys.setenv(TZ = "America/Los_Angeles"))
## cd ~/iCloud/website/data; ./_update_data_themes.sh xrates.qmd
## cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("xrates.qmd")'
## sh ~/iCloud/website/website_short.sh
data(country_money)
country_money <- country_money
country_names <- country_names
country_calling_code <- country_calling_code
codelist <- codelist|>
  transmute(countryname = country.name.en, country_code_2 = fips)

currencycode_countrycode <- country_money|>
  left_join(country_names, by = "ID") |>
  left_join(country_calling_code, by = "ID") |>
  rename(countryname = name) |>
  left_join(codelist, by = "countryname") |>
  transmute(currencycode = isocode, countrycode = country_code_2)

currencycode_countrycode <- tribble(~ currencycode, ~ countrycode,
                                    "USD", "US",
                                    "EUR", "EU",
                                    "JPN", "JP")

currencies <- currencies|>
  filter(locale == "en")


currencies <- currencies|>
  filter(locale == "en")
knitr::opts_chunk$set(echo = T)
xrates <- tribble(
  ~source, ~dataset,
  "bdf",  "EXR",
  "bis",  "EER",
  "bis", "EER_D", 
  "bis",  "XRU",
  "bis",  "XRU_D",
  "ecb",  "EXR",
  "eurostat", "ert_bil_eur_d",
  "eurostat", "ert_h_eur_d",
  "fred",  "xrates",
  "gfd",  "xrates",
  "oecd", "SNA_TABLE4",
  "oecd", "REFSERIES_MSIT",
  "wdi", "PA.NUS.FCRF") |>
  arrange(source, dataset)

save(xrates, file = "xrates.RData")
```


# Info

```{r, echo = F}
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("taux-dinteret.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("interest-rates.qmd")'
# sh ~/iCloud/website/website_short.sh
```


# Current exchange rates

```{r, echo = F, warning = F}
# load_data("public-debt/rating.RData")
"https://www.investing.com/currencies/streaming-forex-rates-majors"|>
  rvest::read_html() |>
  rvest::html_table(header = T, fill = T) |>
  pluck(1) |>
  select(2:4) |>
  #dplyr::left_join(currencycode_countrycode|>
  #                   setNames(c("currencycode1", "countrycode1")),
  #                 by = c("currencycode1")) |>
  #dplyr::left_join(currencycode_countrycode|>
  #                   setNames(c("currencycode2", "countrycode2")),
  #                 by = c("currencycode2")) |>
  mutate(Pair2 = str_replace_all(Pair, "(\\w{2})\\w", "\\1"),
         Pair2 = str_replace(Pair2, "/", ",")) |>
  mutate(Pair3 = Pair) |>
  separate(Pair3, into = c("currencycode1", "currencycode2"), sep = "/") |>
  dplyr::left_join(currencies|>
                     select(currencycode1 = currency_code, symbol1 = currency_symbol),
                   by = c("currencycode1")) |>
  dplyr::left_join(currencies|>
                     select(currencycode2 = currency_code, symbol2 = currency_symbol),
                   by = c("currencycode2")) |>
  select(-currencycode1, -currencycode2) |>
  mutate(symbol1 = paste0("1 ", symbol1, " = ")) |>
  #select(Pair2, symbol1, Bid, symbol2, Pair, Ask) |>
  select(Pair2, symbol1, Bid, symbol2, Pair) |>
  gt::gt() |>
  gt::fmt_flag(columns = Pair2) |>
  gt::cols_width(Pair ~ gt::px(100), Bid ~ gt::px(100), everything() ~ gt::px(60)) |>
  #gt::cols_width(Pair ~ gt::px(100), Bid ~ gt::px(100), Ask ~ gt::px(100), everything() ~ gt::px(60)) |>
  gt::cols_label(Pair2 = "", Pair = "", symbol1 = "", symbol2 = "") |>
  gt::opt_interactive(use_search = F,
                      use_pagination = T,
                      use_pagination_info = F,
                      use_compact_mode = T,
                      page_size_default = 10,
                      page_size_values = c(5, 10, 15, 20)) |>
  gt::tab_footnote(
    footnote = gt::md(paste0("Date: ", format(Sys.time(), format = "%B %d, %Y %I:%M %p"), ". Source: <https://www.investing.com/currencies/streaming-forex-rates-majors>"))
  ) |>
  gt::tab_options(table.width = "100%")
```


## Euros

```{r, echo = F}
"https://www.x-rates.com/table/?from=EUR&amount=1"|>
  rvest::read_html() |>
  rvest::html_table(header = T, fill = T) |>
  pluck(2) |>
  gt::gt() |>
  gt::opt_interactive(use_search = F,
                      use_pagination = T,
                      use_pagination_info = F,
                      use_compact_mode = T,
                      page_size_default = 10,
                      page_size_values = c(5, 10, 15, 20)) |>
  gt::tab_footnote(
    footnote = gt::md(paste0("Date: ", format(Sys.time(), format = "%B %d, %Y %I:%M %p"), ". Source: <https://www.x-rates.com/table/?from=EUR&amount=1>"))
  ) |>
  gt::tab_options(table.width = "100%")
```



## Dollars

```{r, echo = F}
"https://www.x-rates.com/table/?from=USD&amount=1"|>
  rvest::read_html() |>
  rvest::html_table(header = T, fill = T) |>
  pluck(2) |>
  gt::gt() |>
  gt::opt_interactive(use_search = F,
                      use_pagination = T,
                      use_pagination_info = F,
                      use_compact_mode = T,
                      page_size_default = 10,
                      page_size_values = c(5, 10, 15, 20)) |>
  gt::tab_footnote(
    footnote = gt::md(paste0("Date: ", format(Sys.time(), format = "%B %d, %Y %I:%M %p"), ". Source: <https://www.x-rates.com/table/?from=USD&amount=1>"))
  ) |>
  gt::tab_options(table.width = "100%")
```





# Exchange rate of the €

```{r, echo = F}
# cd ~/iCloud/website/data/ecb; /usr/local/bin/Rscript --vanilla _download_one_csv.R EXR; /usr/local/bin/R -e 'quarto::quarto_render("EXR.qmd")'
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -f "xrates.R"; /usr/local/bin/R -e 'quarto::quarto_render("xrates.qmd")'
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R ert_bil_eur_d; /usr/local/bin/R -e 'quarto::quarto_render("ert_bil_eur_d.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## Eurostat

### All

```{r}
ig_d("eurostat", "ert_bil_eur_d", "USD-CHF")
```

### 10 Years

```{r}
ig_d("eurostat", "ert_bil_eur_d", "USD-CHF-10-years")
```

### 1 year

```{r}
ig_d("eurostat", "ert_bil_eur_d", "USD-CHF-1-year")
```


## ECB

### 1998-

```{r}
ig_d("ecb", "EXR", "USD-CHF-GBP")
```

### 1 year

```{r}
ig_d("ecb", "EXR", "USD-CHF-GBP-1-year")
```

### 2 years

```{r}
ig_d("ecb", "EXR", "USD-CHF-GBP-2-years")
```

### 1 month

```{r}
ig_d("ecb", "EXR", "USD-CHF-GBP-1-month")
```

# Exchange rate of the $

```{r, echo = F}
# cd ~/iCloud/website/data/fred; /usr/local/bin/R -f "xrates.R"; /usr/local/bin/R -e 'quarto::quarto_render("xrates.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## Yen

### Long period

```{r}
ig_d("fred", "xrates", "DEXJPUS")
```



### 2000-

```{r}
ig_d("fred", "xrates", "DEXJPUS-2000")
```

## Pound

### Long period

```{r}
ig_d("fred", "xrates", "US-UK-exchange-rate")
```

### 2010-

```{r}
ig_d("fred", "xrates", "US-UK-exchange-rate-2010")
```




# European Countries' exchange rates

```{r, echo = F}
# cd ~/iCloud/website/data/ecb; /usr/local/bin/Rscript --vanilla _download_one_csv.R EXR; /usr/local/bin/R -e 'quarto::quarto_render("EXR.qmd")'
# cd ~/iCloud/website/data/bis; /usr/local/bin/R -f "XRU.R"; /usr/local/bin/R -e 'quarto::quarto_render("XRU.qmd")'
# cd ~/iCloud/website/data/bis; /usr/local/bin/R -f "XRU_D.R"; /usr/local/bin/R -e 'quarto::quarto_render("XRU_D.qmd")'
# cd ~/iCloud/website/data/bis; /usr/local/bin/R -f "EER.R"; /usr/local/bin/R -e 'quarto::quarto_render("EER.qmd")'
# cd ~/iCloud/website/data/bis; /usr/local/bin/R -f "EER_D.R"; /usr/local/bin/R -e 'quarto::quarto_render("EER_D.qmd")'
# sh ~/iCloud/website/website_short.sh
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("xrates.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## Italy, Spain, France, Germany

```{r}
ig_d("bis", "XRU_D", "XRU-DEU-ESP-FRA-ITA")
```


## Poland, Hungary

### All

```{r}
ig_d("bis", "XRU_D", "POL-HUN-DEU")
```

### 1995-

```{r}
ig_d("bis", "XRU_D", "POL-HUN-DEU-1995")
```


# Emerging economies' exchange rates


```{r, echo = F}
# cd ~/iCloud/website/data/bis; /usr/local/bin/R -f "XRU_D.R"; /usr/local/bin/R -e 'quarto::quarto_render("XRU_D.qmd")'
# sh ~/iCloud/website/website_short.sh
```

## Russian ruble

```{r}
ig_d("bis", "XRU_D", "RUS")
```


## Columbian peso

```{r}
ig_d("bis", "XRU", "COL")
```

# Effects of events on exchange rates


```{r, echo = F}
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R ert_h_eur_d; /usr/local/bin/R -e 'quarto::quarto_render("ert_h_eur_d.qmd")'
# cd ~/iCloud/website/data/ecb; /usr/local/bin/Rscript --vanilla _download_one_csv.R EXR; /usr/local/bin/R -e 'quarto::quarto_render("EXR.qmd")'
# cd ~/iCloud/website/data/bis; /usr/local/bin/R -f "XRU.R"; /usr/local/bin/R -e 'quarto::quarto_render("XRU.qmd")'
# cd ~/iCloud/website/data/bis; /usr/local/bin/R -f "XRU_D.R"; /usr/local/bin/R -e 'quarto::quarto_render("XRU_D.qmd")'
# cd ~/iCloud/website/data/bis; /usr/local/bin/R -f "EER.R"; /usr/local/bin/R -e 'quarto::quarto_render("EER.qmd")'
# cd ~/iCloud/website/data/bis; /usr/local/bin/R -f "EER_D.R"; /usr/local/bin/R -e 'quarto::quarto_render("EER_D.qmd")'
# cd ~/iCloud/website/data/bis; /usr/local/bin/R -f "EER_M.R"
# sh ~/iCloud/website/website_short.sh
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("xrates.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
```

## Germany's revaluation of 1961

```{r}
ig_d("bis", "XRU_D", "DEU-USA-1961")
```


## September 2, 1985 - Plaza accords

### Germany, France, UK

```{r}
ig_d("bis", "XRU_D", "plaza-accords-1980-1990")
```

### Canada, Italy, Spain

```{r}
ig_d("bis", "XRU_D", "plaza-accords-1980-1990-CAN-ITA-ESP")
```



## Switzerland, Jan. 15, 2015

On Jan. 15, 2015, Switzerland announced that it was going to scrap its currency peg of 1.20 to the euro.

```{r}
ig_d("eurostat", "ert_bil_eur_d", "USD-CHF-2014-2015")
```




## Effects of Brexit referendum: June 23, 2016

```{r}
ig_d("bis", "XRU_D", "GBR-USA-2015-2018")
```


## Effects of Trump election: November 8, 2016

```{r}
ig_d("bis", "XRU_D", "GBR-USA-2016-2017")
```





# Comparing different sources for xrates: creation of €

```{r, echo = F}
# cd ~/iCloud/website/data/wdi; /usr/local/bin/Rscript --vanilla _dl_one2.R PA.NUS.FCRF; /usr/local/bin/R -e 'quarto::quarto_render("PA.NUS.FCRF.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("xrates.qmd")'
# cd ~/iCloud/website/data/wdi; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
# cd ~/iCloud/website/data/eurostat; /usr/local/bin/Rscript --vanilla _download_one.R ert_h_eur_d; /usr/local/bin/R -e 'quarto::quarto_render("ert_h_eur_d.qmd")'
# cd ~/iCloud/website/data/oecd; /usr/local/bin/Rscript --vanilla _download_data.R SNA_TABLE4; /usr/local/bin/R -e 'quarto::quarto_render("SNA_TABLE4.qmd")'
# cd ~/iCloud/website/data/oecd; /usr/local/bin/Rscript --vanilla _download_data.R REFSERIES_MSIT; /usr/local/bin/R -e 'quarto::quarto_render("REFSERIES_MSIT.qmd")'
# sh ~/iCloud/website/website_short.sh
```




## BIS

```{r}
ig_d("bis", "XRU_D", "DEU-ESP-FRA-ITA-GRC")
```

## Eurostat

```{r}
ig_d("eurostat", "ert_h_eur_d", "DEM-FRF")
```

## OECD

### SNA_TABLE4

```{r}
ig_d("oecd", "SNA_TABLE4", "FRA-DEU-ITA-ESP-GRC")
```

### REFSERIES_MSIT

```{r}
ig_d("oecd", "REFSERIES_MSIT", "FRA-DEU-ITA-ESP-GRC")
```

## WDI

```{r}
ig_d("wdi", "PA.NUS.FCRF", "FR-DE-IT-ES-GR")
```

```{r, echo = F}
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("public-debt.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("employment.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("index.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("xrates.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("monetary-policy.qmd")'
# cd ~/iCloud/website/data; /usr/local/bin/R -e 'quarto::quarto_render("industry.qmd")'
# sh ~/iCloud/website/website_short.sh
```



